### 2016-08-20 src/acoustic-2d-fortran/paper.tex
add acoustic-3d-cpu code

\title{Approximating Q propagation to speed up finite differences}
\author{Robert G. Clapp}
\righthead{Approximate Q}
\lefthead{Clapp}
\footer{SEP--158}
\maketitle

\begin{abstract}

%Motivation

Propagating wave-fields using explicit finite difference is the kernel for Reverse Time Migration (RTM) and high end velocity analysis
algorithms.
To avoid grid dispersion artifacts,  the cost of propagation is proportional to the frequency of the energy being propagated raised
to the fourth power.
Attenuation in the earth tends to decrease usable frequencies as a function of time.
By using an approximation to the wave equation for attenuated media, to save computation, we can approximate the earth's behavior.
As a result we can use coarser sampling at large time. Combined
with limiting  grid propagation to around the source at early times we can achieve large speedups in modeling, migration, and potentially
velocity analysis.
\end{abstract}

%Approach
%Results
%Conslussions

\section{Introduction}
Imaging and velocity analysis are the most computationally intensive parts
of seismic processing. As a results researchers are always trying
to find ways to speedup these processes \cite[]{bednar,Stork}.
One approach used to speed up downward continuation based
algorithms is to recognize that the earth attenuates seismic signals.
As a result, as we push the wave-field down in depth, we can ignore
higher and higher frequencies and still obtain an accurate image\cite[]{Clapp.sep.111.bob3}.
This approach lowers the cost as you increase in depth. This technique is well
suited for downward continuation based approaches which are done
frequency by frequency.
Reducing the frequencies downward
continued as a function of depth  is particularly effective in combination with recognizing
that there was no reason to propagate waves a large distance from
the source at early times. 
While following the wavefield is used routinely in RTM,  taking
advantage of attenuation is not commonly used.  Reasons include:
the cost of propagation with an attenuated wave equation, 
attenuation is a function of medium parameter, and propagation 
is generally done in the the time, rather frequency domain.
\par
In this paper I use a constant-Q approximation based on the work of \cite{zhu}.  As
I propagate my source I resample my medium based on the maximum frequency that has not
been significantly attenuated. Combining this approach with following the wave-field,
I show that I can achieve significant computational speedups.

\section{Modeling}

Explicit finite difference modeling is constrained by figuring  out a sampling in time and space that results in stable propagation and does not create dispersive events.  For stability the Courant-Friedrichs-Lewy condition \cite[]{courant1967partial} must be met. 
Stability is a function of limiting what percentage of a grid cell energy can move in one time step. Stability is therefore a function of the maximum velocity 
$v_{max}$, the minimum spatial sampling 
$d_{min}$, and the time step $dt$. For stability,
\begin{equation}
v_{max}\frac{dt}{d_{min}} < .5 \label{eq:stability}.
\end{equation}
The stability condition pushes one to use larger spatial sampling (faster, but less resolution) and/or finer time sampling (more expensive).  Dispersion, on the other hand, is a function of the minimum velocity $v_{min}$, the maximum frequency $f_{max}$, and the maximum spaital sampling $d_{max}$.   To avoid grid dispersion we need to  sample a given frequency with a minimum number of points.  There isn't a consensus on the minimum number
of points. For the purpose of this paper I will require  3.2  points therefore,
\begin{equation}
\frac{v_{min} }{f_{max}d_{max}} > 3.2 \label{eq:dispersion}. 
\end{equation}
The dispersion constraint pushes us towards smaller (more expensive) spatial sampling, because of the stability constraint, and results in smaller the
steps.
Minimizing dispersion is the real reason for the expense of finite differences.  To avoid grid dispersion and achieve the same level of stability the number of operations increase by the fourth power (three due to space sampling and one for time).
\par
From observation we know that the earth attenuates acoustic signals.  Attenuation varies as a function of frequency and earth materials. The first approximation I am going to use is the concept of the constant
Q model introduced by \cite{Kjartansson.sep.23}. 
Q is defined as
\begin{equation}
Q=2 \pi \left( \frac{E}{\partial E}\right),
\end{equation}
where $\frac{E}{\partial E}$ is the fraction of energy lost per cycle. The larger the $Q$ value, the less energy loss per cycles.
 The constant Q assumption assumes that energy dies out is a function of the number of wavelengths traveled through a medium. The higher the frequency, the faster the energy is attenuated.
\subsection{Constant-Q Formulation}
Building on this foundation \cite{zhu} used a fractional Laplacian approach to perform attenuated  propagation 
in the time domain. Given a forcing function $f(t)$ and the wave-field $P(t)$ they proposed the equation,
\begin{equation}
\left[ \eta \bf L + \tau \bf H \frac{d}{dt} - v^{-2} \frac{\partial^2}{\partial t^2}\right] P(t)=f(t) \label{eq:zhu1},
\end{equation}
where 
\begin{eqnarray}
\bf L = \left(-\nabla^2\right)^{\gamma+1} \\
\bf H = \left(-\nabla^2\right)^{\gamma+\frac{1}{2}}.
\end{eqnarray}
The constants in equation \ref{eq:zhu1} are defined as 
\begin{equation}
\eta=-v^{2\gamma}w_0^{-2\gamma} \cos \pi \gamma,
\end{equation}

\begin{equation}
\tau=-v^{2\gamma-1}w_0^{-2\gamma} \sin \pi \gamma,
\end{equation}
and 
\begin{equation}
\gamma=\frac{1}{\tan^{-1}\frac{1}{Q}}.
\end{equation}
The first term in equation \ref{eq:zhu1} deals the dispersive effect of attenuation. The middle term
deals damping.  For a constant Q approximation I can further simplify equation~\ref{eq:zhu1}, approximating
$\nabla^2$ for $\bf H$. My resulting equation is then
\begin{equation}
\left[ \nabla^2 - \tau \nabla^2 \frac{d}{dt} - v^{-2} \frac{\partial^2}{\partial t^2}\right] P(t) =f(t) \label{eq:use}.
\end{equation}
\par
Figure \ref{fig:qnoq} shows the wave-field using the standard acoustic wave equation (left) and an attenuation wave-field (right). Note
the difference in the frequency content. This is can be more clearly seen in
Figure \ref{fig:spectra} which shows the spectrum of wave-field at $.3,1.3,2.3$, and $3.3$ seconds with $Q=200$. Notice the energy
decay of frequency over time. 
The key observation is that there is no reason to worry about dispersion at frequencies that have attenuated. Specifically, I  redo my dispersion calculation (equation \ref{eq:dispersion}) several times while propagating
a wave-field. At each time block I use a $f_{max}$ based on frequencies whose energy has not been reduced more than some percentage (in this paper 96\%).  As a result,  as I forward propagate in time my grid cells, and if I desire,  time sampling,
get larger.  
Figure~\ref{fig:timeQ} shows the speedup factor (defined as the number of grid cells times time steps) as a function of propagation time for different Q values.  The longer the time record, the more using Q pays off in terms speed up. 
Using this approach the early time steps dominate the computation.  For example assuming an initial maximum frequency of 
$90Hz$ and a constant velocity of $2000 m/s$, a Q value of $200$, the total speedup is $4$ even though  most of the 
propagation time  shows significantly more speedup. Figure~\ref{fig:qtot} shows the speedups for Q values ranging from 150 to 350.

\plot{qnoq}{width=6.0in}{The wave-field with the standard acoustic wave equation (left) and the attenuated wave-field (right) at the same time.\ER}

\sideplot{spectra}{width=3.0in}{The frequency of the wave-field at various times.  Note the reduction of the high frequencies over time. Note at .3 seconds,
total amplitude is less because the source has not been fully injected into the medium.\ER}

\sideplot{timeQ}{width=2.5in}{Speedup values as a function of propagation time for Q values ranging from 150 to 350.  Note how the longer the time record the more the computation is sped up.\ER}
\sideplot{qtot}{width=2.5in}{Total speedup for different values of Q.  Note the relatively small speedups compared to what one might expect looking at Figure~\ref{fig:timeQ}.  Total time is the inverse of the sum of the inverses of speedups.\ER}
\par
Another speedup trick used by many when doing modeling/migration is to recognize that there is no need to propagate the wave-fields significantly away from the source
at early times.  The number of cells we need to propagate increases as a  power of three (expanding wave-field)
in modeling, and somewhat less in migration due to the spatial extent of our receivers.
This speedup trick is most effective at early times and useless at late times when energy has propagated throughout the model, the  opposite
behavior as the constant-Q trick. Figure~\ref{fig:follow}  shows a typical wide azimuth geometry and
the speedup as a function of time again assuming $2 km/s$ medium. Total speedup for
following the source is only 2-2.5.   
Combining the two tricks is where we begin to see big payoffs.
The left plot of Figure~\ref{fig:timeTot} shows the result of combining the two approaches for different values of
Q.  The right plot shows the total speedup as a function of Q.  Note how the maximum cost is in the $1$ to $3$ second range
depending on the value of Q.  Without following the wave-field the total speedup ranged from  1.8 to 4, we now get speedups between 15 and 250.
\sideplot{follow}{width=2.5in}{Speedup by following the wave-field in the case of modeling a single shot and in the case of an array of receivers. Note how
these curves move in the opposite direction to those in Figure~\ref{fig:timeQ}.\ER}
\plot{timeTot}{width=6.0in}{The left plot shows speed up as a function of propagation time for a series of Q values. The right plot shows the total
speedup as a function of Q. Note on the left how total speedup is a combination of the trends shown in Figures~\ref{fig:timeQ} and \ref{fig:follow}. Note
on the right the significant speedup compared to those shown in Figure~\ref{fig:qtot}.\ER} Calculating speedup numbers is far from an exact science. My choice of a low constant velocity helps me by improving the speedups due to following the wave-field and hurts me by allowing larger time steps.  Computational
time and the number of grid cells do not completely linear relation. Smaller grids, means better cache behavior, and can lead
to significant improvements in performance. In addition my propagator is more
expensive than the standard acoustic propagator which isn't taken into account.

\begin{algorithm} \caption{Forward propagation} \label{alg:forward}
\begin{algorithmic}[1]
\FOR{timeblock 0...n}
\STATE{Calculate max frequency of interest relevant at the beginning of time window}
\STATE{Calculate max extent of wave-field at end of time window}
\STATE{Calculate sampling of medium and time based on stability/dispersion constraints}
\STATE{Resample wave-field and velocity}
\FOR {t=0...n in timeblock}
\STATE{ Propagate wave-field with Q approximation}
\STATE{Inject source}
\IF{Imaging step}
\STATE{Store wave-field}
\ENDIF
\ENDFOR
\ENDFOR
 \end{algorithmic}
\end{algorithm}

The basic algorithm for modeling is shown in Algorithm~\ref{alg:forward}.  Figure~\ref{fig:sampleCompare} shows the wave-field propagating through
a relatively complex synthetic after 2 seconds using resampling tricks (left) and a static grid (right).  
\plot{sampleCompare}{width=6.0in}{The left panel shows the wave-field using a static grid, the 
right panel using the approach outline in algorithm~\ref{alg:forward} both using equation~\ref{eq:use}. Note the low frequency artifact in the right panel, but otherwise
the plots are nearly identical.\ER}

\section{Migration}
Applying the method described above to RTM is relatively straightforward. Modeling is done using the
approach outlined in algorithm~\ref{alg:forward}.  Back propagation starts with low frequencies
and then increases in frequency at smaller times.  For real data there is no need to 
use the approximate Q propagator because the whole assumption of this approach is that
there is no useful information at high frequencies at large times. The back projection 
step is described in algorithm~\ref{alg:backward}.

\begin{algorithm} \caption{Backward propagation for real data}\label{alg:backward}
\begin{algorithmic}[1]
\FOR{timeblock n...0}
\STATE{Calculate max frequency of interest relevant at the beginning of time window}
\STATE{Calculate max extent of wave-field at end of time window}
\STATE{Calculate sampling of medium and time based on stability/dispersion constraints}
\STATE{Resample wave-field, velocity}
\STATE{Resample temp image to full image and sum}
\STATE{Create temp image}
\FOR {t=n..0 in timeblock}
\STATE{ Propagate wave-field}
\STATE{Inject source}
\IF{Imaging step}
\STATE{Apply imaging condition store in temp image}
\ENDIF
\ENDFOR
\ENDFOR
 \end{algorithmic}
\end{algorithm}
Figure~\ref{fig:single} shows the result of migrating a single shot using a standard static grid, left, and a changing grid, right.  There is significantly
more noise, particularly away from the main energy train, using the variable grid, but the main energy train is nearly identical. Figure~\ref{fig:full}
shows the result of migrating an entire dataset using the changing grid method. After summing all the shots the artifacts seen in Figure~\ref{fig:single}
have disappeared.
\plot{single}{width=6.0in}{The left plot shows the result of migrating a single shot using a static grid, the right plot shows the result using
the changing grid described by algorithms \ref{alg:forward} and \ref{alg:backward}.  Note the spurious energy away from the main energy
train using the changing grid.\ER}
\plot{full}{width=6.0in}{The result of migrating an entire dataset using the changing grid approach. Note how the artifacts seen in Figure~\ref{fig:single}
are not apparent in the final migration.\CR}
\section{Discussion}
The tests shown in this paper are limited to modeling and migration. Another obvious area to apply
these techniques is velocity analysis. For waveform inversion techniques that rely on low frequencies this approach
will lead to minimal speedup advantages but the cheap approximation of attenuation might prove useful.
The big advantage is for  Wave Equation Migration Velocity Analysis\cite[]{Zhang.sep.152.yang1} and Total Full Waveform Inversion\cite[]{Almomin.sep.155.ali1} techniques.
In addition to potentially a better approximation of matching the physics of the real data, these technique
are interested in large time records and higher frequencies, which is where this approach leads to significant performance
improvments.  The reduction in data size,  resulting
from coarser sampling of the wave-field could also prove useful.

\section{Conclusions}
I use an approximation to \cite{zhu} to simulate propagation in an attenuated earth. I take
advantage of the fact that frequencies decay with time by resampling my propagation grid
at later times. Combining this approach with following the wave-field leads to
significant speedups in modeling and RTM. The approach is also
potentially useful for Wave Equation Migration Velocity Analysis and Total
Full Waveform Inversion.

\section{Acknowledgements}
I would like to thank Yi Shen for the time-domain approximate-Q formulation and Gustavo Alves for
the initial discussion that brought on this idea. I would like than Total for providing the
data used in this paper.

\bibliographystyle{seg}
\bibliography{SEP,bob}

### 2016-08-20 src/acoustic-2d-fortran/box_mod.f90

@@ -1,0 +1,324 @@
+module box_mod
+  use modeling_mod
+  use sep
+  use vel_mod
+  use data_mod
+  use source_mod
+  implicit none
+  logical, private :: v
+  real, private :: vmin,vmax,dmin,dmax
+  double precision :: tot1Cells,tot2Cells
+  integer :: totImaging
+  integer,private :: timeBlocks
+  real,private :: dstable
+  integer :: slow
+  integer, private :: bound,error,jimage
+  real,private :: errorFact,downFact,qfact,maxF,dtBig
+  real, pointer :: sincT(:,:)
+
+  type timesT
+    integer :: n1,n2,n3
+    real    :: o1,o2,o3
+    real    :: d1,d2,d3
+    real,allocatable :: vals(:,:,:)
+  end type
+
+  type boxT
+    type(modelingT), pointer :: hyper(:)
+    integer :: nt
+    real    :: dt
+    integer :: totImaging
+    real :: blockSize
+
+  end type
+
+  interface
+    subroutine fastmarch(order,s1,s2,s3,b1,b2,b3,n1,n2,n3,d1,d2,d3,s0,slow,ttime) bind(c,name="fastmarch")
+      import
+      real(c_float),intent(in),value:: s1,s2,s3,d1,d2,d3,s0
+      integer(c_int), value,intent(in) :: order,b1,b2,b3,n1,n2,n3
+      real(c_float),dimension(*) :: slow,ttime
+    end subroutine
+  end interface
+
+contains
+
+  subroutine initTimes(timesS)
+    type(timesT) :: timesS
+    integer :: ierr
+    character(len=128) :: label 
+    ierr=sep_get_data_axis_par("times",1,timesS%n1,timesS%o1,timesS%d1,label)
+    ierr=sep_get_data_axis_par("times",2,timesS%n2,timesS%o2,timesS%d2,label)
+    ierr=sep_get_data_axis_par("times",3,timesS%n3,timesS%o3,timesS%d3,label)
+    allocate(timess%vals(timess%n1,timess%n2,timess%n3))
+    ierr=sreed("times",timesS%vals,size(timesS%vals)*4)
+
+  end subroutine
+
+  subroutine cleanBoxShot(boxS)
+    type(boxT) :: boxS
+    integer :: i
[…]

### 2016-08-20 src/acoustic-2d-fortran/data_mod.f90

@@ -1,0 +1,108 @@
+module data_mod
+  use modeling_mod
+  use sep_mod
+  use sep
+  implicit none
+
+  type dataT
+    integer :: n1,n2,n3
+    real :: o1,o2,o3
+    real :: d1,d2,d3
+    real :: depth
+    real,allocatable :: dat(:,:)
+    real,allocatable :: floc(:,:)
+    character(len=128) :: tag
+  end type
+
+contains
+
+  subroutine initData(tag,dat)
+    character(len=*) :: tag
+    type(dataT) :: dat
+    integer :: nx,ny,i2,nt,ns
+    real :: ox,oy,dx,os,ds
+    integer :: ierr,i
+    real, allocatable :: tmp(:,:)
+    real :: ot,dt,depth,x,y
+    character(len=128) :: tmpS
+
+    ierr= sep_get_data_axis_par(tag,1,dat%n1,dat%o1,dat%d1,tmpS)
+    ierr= sep_get_data_axis_par(tag,2,dat%n2,dat%o2,dat%d2,tmpS)
+    ierr= sep_get_data_axis_par(tag,3,dat%n3,dat%o3,dat%d3,tmpS)
+    dat%tag=tag
+
+
+    call from_param("depth",dat%depth,0.)
+    allocate(dat%floc(2,dat%n2))
+    allocate(dat%dat(dat%n1+10,dat%n2))
+  end subroutine
+
+
+  real function getShotLocation(dat,ishot) result(res)
+    type(dataT) :: dat
+    integer :: ishot
+
+    res=dat%o3+dat%d3*(ishot-1)
+  end function
+
+  subroutine readShot(dat,ishot)
+    type(dataT) :: dat
+    integer :: ishot
+    integer :: ierr,i2
+    real :: x
+    real,allocatable :: tmp(:,:)
+    integer :: ng(3),nw(3),fw(3),jw(3)
+    jw=1
+    fw=0
+    ng=(/dat%n1,dat%n2,dat%n3/)
+    nw=ng
+    nw(3)=1
+    fw(3)=ishot-1   
+
+
+    !ierr=sseek_block(dat%tag,ishot,dat%n2*dat%n1*4,0)
+
+    ! ASK: why calculate x and dat%floc
+    do i2=1,dat%n2
[…]

### 2016-08-20 src/acoustic-2d-fortran/diff.f90

@@ -1,0 +1,18 @@
+program ab
+use sep
+integer :: n1,n2
+real, allocatable :: in(:,:),out(:,:)
+integer :: i1,ierr
+
+call sep_init()
+call from_history("n2",n2)
+call from_history("n1",n1)
+allocate(in(n1,n2),out(n1,n2))
+ierr=sreed("in",in,size(in)*4)
+out(1:n1-1,:)=in(2:,:)-in(1:n1-1,:)
+out(n1,:)=out(n1-1,:)
+
+
+ierr=srite("out",out,size(in)*4)
+
+end program

### 2016-08-20 src/acoustic-2d-fortran/main.f90

@@ -1,0 +1,58 @@
+program RTM_FAST
+  use migrate_shot_mod
+  use sep
+  logical :: verb
+  type(velT) :: vel
+  type(timesT) :: times
+  type(sourceT) :: source
+  type(dataT)   :: dat
+  type(modelingT) :: full
+  integer :: ishot,ii
+  real :: factor,rnd
+  integer, allocatable :: shot(:)
+  logical, allocatable :: shotL(:)
+  
+  
+  call initpar()
+  call setup_timers()
+  
+  !SETUP global migration parameters
+  call start_timer_num(timerInit)
+  call from_param("verbose",verb,.false.)
+  call readVel("vel",vel,full)
+  call initData("data",dat)
+  call calcImage(vel,"img")
+  call readSource("source",source)
+  call initTimes(times)
+  call initBox(dat,source,vel,verb)
+  
+  call  init_sinc_table(8,10000)
+  call stop_timer_num(timerInit)
+  
+  
+  allocate(shot(dat%n3),shotL(dat%n3))
+  shotL=.false.
+  ishot=1
+  do while(ishot<=dat%n3)
+    call random_number(rnd)
+    ii=max(1,min(dat%n3,nint(rnd*dat%n3)+1))
+    if(.not. shotL(ii)) then
+      shot(ishot)=ii
+      ishot=ishot+1
+    end if
+  end do
+  
+  
+  do ishot=1,dat%n3
+      factor= migrate_shot(shot(ishot),verb,vel,dat,source,times)
+      write(0,*) ishot," MIGRATING SHOT", shot(ishot), " of ",dat%n3, " sped up ",factor
+      if(mod(ishot,5)==0)  call writeFullImage("img")
+  end do
+  call print_timers()
+  call writeFullImage("img")
+  
+end program
+  
+  
+  
+  

### 2016-08-20 src/acoustic-2d-fortran/mig_shot.f90

@@ -1,0 +1,253 @@
+module migrate_shot_mod
+  use sep
+  use vel_mod
+  use prop_mod
+  use my_timers_mod
+  use image_mod
+  use box_mod
+  use data_mod
+  use source_mod
+  implicit none
+  logical, private :: qtest
+  integer,private  :: writeSection,icount
+  integer, private :: writeCheckPoint
+
+contains
+
+  real function migrate_shot(ishot,verb,vel,dat,source,times) result(factor)
+    integer :: ishot
+    logical :: verb
+    type(velT) :: vel,vuse
+    type(dataT) :: dat
+    type(sourceT) :: source
+    type(timesT)  :: times
+    type(imageT) :: iuse
+    type(boxT)  :: domain
+    type(waveT), target :: p1,p2,p3
+    type(waveT), pointer :: pold,pcur,pnew
+    type(modelingT),pointer :: cur,old
+    type(modelingT) :: full
+    type(sourceW) :: sou
+    integer :: iblock,it,iimage,slow,ierr
+    logical :: xx
+    real :: t0
+    full%o1=vel%o1; full%d2=vel%d2 ;full%n2=vel%n2;
+    full%o2=vel%o2; full%d1=vel%d1; full%n1=vel%n1
+    call start_timer_num(timerIS)
+    call readShot(dat,ishot)
+    call setSourceLocation(source, getShotLocation(dat,ishot))
+    call from_param("qtest",qtest,.false.)
+    call from_param("writeSection",writeSection,-1)
+    call from_param("writeCheckpoint",writeCheckpoint,-1)
+    icount=0
+    factor=calcShotBox(vel,dat,source,times,domain)
+    cur=>domain%hyper(1); old=>cur
+    if(writeCheckPoint>0) then
+      ierr= sep_put_data_axis_par("wfield",1,vel%n1,vel%o1,vel%d1,"Depth");
+      ierr= sep_put_data_axis_par("wfield",2,vel%n2,vel%o2,vel%d2,"X Position");
+    end if
+
+    call initWavefields(cur,p1,p2,p3)
+    call initSourceSave(sou,domain%totImaging)
+    if(writeSection>0) then
+      ierr= sep_put_data_axis_par("wfield",1,vel%n1,vel%o1,vel%d1,"Depth");
+      ierr= sep_put_data_axis_par("wfield",2,vel%n2,vel%o2,vel%d2,"X Position");
[…]

### 2016-08-20 src/acoustic-2d-fortran/prop_mod.f90

@@ -1,0 +1,183 @@
+module prop_mod
+  use modeling_mod
+  use resampleMod
+  use vel_mod
+  use sep
+  implicit none
+  real, private :: factor,gamma
+  real, private :: b_b(20)
+  type waveT
+    real,allocatable :: dat(:,:)
+  end type
+   
+  interface
+
+ end interface
+  
+  contains
+  
+subroutine initWavefields(cur,p1,p2,p3)
+  type(modelingT) :: cur
+  type(waveT) :: p1,p2,p3
+    allocate(p1%dat(cur%n1,cur%n2))
+    allocate(p2%dat(cur%n1,cur%n2))
+    allocate(p3%dat(cur%n1,cur%n2))
+end subroutine
+
+subroutine cleanWavefields(p1,p2,p3)
+  type(waveT) :: p1,p2,p3
+  deallocate(p1%dat,p2%dat,p3%dat)
+end subroutine
+  
+subroutine propWave(prev,cur,new,vsq,d1a,d2a,d0,b,e,b1,e1)
+  real  :: prev(:,:),cur(:,:),new(:,:),vsq(:,:)
+  double precision  :: d1a(:),d2a(:)
+  real   ::d0,gamma,factor
+  integer :: b(:),e(:),b1,e1
+  real ::d11,d12,d13,d14,d15,d21,d22,d23,d24,d25
+  integer :: i1,i2
+  real :: tau,taucur,tauprev
+  
+  d11=d1a(1); d12=d1a(2); d13=d1a(3); d14=d1a(4); d15=d1a(5);
+  d21=d2a(1); d22=d2a(2); d23=d2a(3); d24=d2a(4); d25=d2a(5);
+  
+!  write(0,*) "CHECK D11",d11,d21
+ ! call seperr("")
+  do i2=b(2),e(2)
+   do i1=b(1),e(1)
+     new(i1,i2)=vsq(i1,i2)*(&
+       d11*((cur(i1-1,i2)+cur(i1+1,i2)))+&
+       d12*((cur(i1-2,i2)+cur(i1+2,i2)))+&
+       d13*((cur(i1-3,i2)+cur(i1+3,i2)))+&
+       d14*((cur(i1-4,i2)+cur(i1+4,i2)))+&
+       d15*((cur(i1-5,i2)+cur(i1+5,i2)))+&
[…]

### 2016-08-20 src/acoustic-2d-fortran/random_mod.f90

@@ -1,0 +1,119 @@
+module randomMod
+implicit none
+
+contains
+subroutine addRandom(vel,bnd)
+  real :: vel(:,:)
+  integer :: bnd,ie1,ie2
+  real,allocatable :: my_rand(:)
+  real :: vmin,f
+  real :: idist,mys
+  integer :: nrand,nlen
+  integer :: i1,i2,irand,i,id2,id1
+  integer :: n1,n2
+  real,allocatable :: mymean(:)
+  
+  nrand=max(size(vel,1),size(vel,2))
+  allocate(mymean(2*nrand))
+  mymean=0
+  vmin=minval(vel)
+  nrand=nrand*nrand*6
+  allocate(my_rand(nrand))
+  call random_number(my_rand)
+  irand=1
+  do i1=1,size(mymean)
+    mymean(i1)=vmin*.1*(real(i1)/real(size(mymean)))
+  end do
+  n1=size(vel,1)
+  n2=size(vel,2)
+
+  
+
+
+    do i2=1,size(vel,2)
+      id2=0
+      if(i2 <=bnd) then
+        id2=i2-bnd+1
+        ie2=bnd+1
+      end if
+      if(i2> size(vel,2)-bnd) then
+        id2=bnd-(size(vel,2)-i2)
+        ie2=size(vel,2)-bnd
+      end if
+      do i1=1,size(vel,1)
+        id1=0
+        if(i1 <=bnd) then
+          id1=i1-bnd+1
+          id1=bnd+1
+        end if
+        if(i1> size(vel,1)-bnd) then
+          id1=bnd-(size(vel,1)-i1)
+          ie1=size(vel,1)-bnd
+        end if
+        idist=id1*id1+id2*id2
+        if(idist>0) then
+          idist=sqrt(idist)
+          f=real(idist)/real(size(mymean))
+          vel(i1,i2)=.5*vel(ie1,ie2)*my_rand(irand)+&
+            (1.-f)*vel(ie1,ie2)+f*mymean(idist)
+          irand=irand+1
+        end if
+    end do
+  end do
+
+
+
+  do i2=1,size(vel,2)
+    !smooth top
+    mys=vel(bnd+1,i2)*bnd*2
+    nlen=bnd*2+1
+    do i1=bnd,1,-1
[…]

### 2016-08-20 src/acoustic-2d-fortran/resample_mod.f90

@@ -1,0 +1,169 @@
+module resampleMod
+  use modeling_mod
+  use sinc_mod
+  implicit none
+  real, allocatable :: sinc_table(:,:)
+  integer,private :: ns
+
+contains
+
+  subroutine init_sinc_table(nsinc,npts)
+    integer :: nsinc,npts
+    real    :: loc
+    integer :: n,i
+
+    allocate(sinc_table(nsinc,npts))
+    ns=nsinc
+    call mksinc_table(npts,nsinc,sinc_table)
+  end subroutine
+
+
+  subroutine interpField(oldS,newS,oldF,newF,extend)
+    logical :: extend
+    type(modelingT) :: oldS,newS
+    real :: oldf(:,:), newf(:,:)
+    integer,allocatable:: t3(:),t2(:),t1(:)
+    integer :: i1,i2,i3,b3,e3,b2,e2,b1,e1
+    integer ia,ib,ic
+    integer,allocatable ::c2(:,:),c1(:,:)
+    real,allocatable :: x1(:),x2(:)
+    integer,allocatable :: k1(:),k2(:)
+    allocate(x2(newS%n2),x1(newS%n1))
+    b2=newS%n2; b1=newS%n1;
+    e2=1; e1=1;
+    newf=0;
+
+    do i2=1,newS%n2
+      x2(i2)=(newS%o2+newS%d2*(i2-1.)-oldS%o2)/oldS%d2+1
+      if(x2(i2) > .999 .and. i2 < b2) b2=i2
+      if(x2(i2) < oldS%n2+.001 .and. i2 > e2) e2=i2
+    end do
+    do i1=1,news%n1
+      x1(i1)=(newS%o1+newS%d1*(i1-1.)-oldS%o1)/oldS%d1+1
+      if(x1(i1) > .999 .and. i1< b1) b1=i1
+      if(x1(i1) < oldS%n1+.001 .and. i1 > e1) e1=i1
+    end do
+    allocate(k1(newS%n1),k2(newS%n2))
+    !!write(0,*) "OLD 1",oldS%n1,oldS%o1,oldS%d1
+    !write(0,*) "NEW 1",newS%n1,newS%o1,newS%d1
+    !write(0,*) "MAP 1",minval(x1),maxval(x1)
+
+    !write(0,*) "OLD 2",oldS%n2,oldS%o2,oldS%d2
[…]

### 2016-08-20 src/acoustic-2d-fortran/sinc_bob.c

@@ -1,0 +1,94 @@
+#include<math.h>
+#include<stdio.h>
+void mksinc (float *sinc,int lsinc,float d,float *space);;
+void toep (int m,float *r,float *f,float *g,float *a);
+
+/************************************************************************
+ *                          Subroutine mksinc                            *
+ *************************************************************************
+ * Derives tapered sinc interpolator coefficients by least squares       *
+ * spectral matching.  Theory in WGC technical document by Larner, 1979. *
+ *  Dave Hale, 1/31/83                                                   *
+ *************************************************************************
+ *   sinc    tapered sinc interpolation coefficients                     *
+ *   lsinc   length of sinc -- MUST BE EVEN; lsinc<20 RECOMMENDED!       *
+ *   d       fractional distance to interpolated point; 0<=d<=1 REQUIRED!*
+ *   space   workspace of lsinc*3 floats                                 *
+ *************************************************************************
+ *After calling mksinc, use the coefficients to interpolate as follows:  *
+ *                    j=lsinc-1                                          *
+ * y(t) = y(i+d) =      sum     sinc[j]*y[i+j-lsinc/2+1]                 *
+ *                      j=0                                              *
+ ************************************************************************/
+void mksincit (float *sinc,int lsinc,float d,float *space)
+{
+  int j;
+  float *b,*c,*work,pi,pi2,snyq,snat,s0,ds,eta,s;
+
+  /* compute constants */
+  pi = 3.141592654;
+  pi2 = pi*2;
+  snyq = 0.5;
+  snat = snyq*(0.066+0.265*log((double)lsinc));
+  s0 = 0.0;
+  ds = (snat-s0)/(lsinc*2-1);
+  eta = lsinc/2-1.0+d;
+
+  /* segment work space */
+  b = space; c = b+lsinc; work = c+lsinc;
+
+  /* compute coefficients of Toeplitz linear system */
+  for (j=0; j<lsinc; j++){
+    for (s=s0,b[j]=c[j]=0.0; s<=snat; s+=ds)
+    {
+      b[j] += cos(pi2*s*j);
+      c[j] += cos(pi2*s*(eta-j));
+    }
+  }
+
+  /* solve the system for sinc coefficients */
+  toep (lsinc,b,sinc,c,work);
+
+}
+
+
[…]

### 2016-08-20 src/acoustic-2d-fortran/sinc_mod.f90

@@ -1,0 +1,30 @@
+module sinc_mod
+
+  implicit none
+
+  interface
+    subroutine mksincit(sinc,lsinc,d,space) bind(c,name="mksincit")
+      use iso_c_binding
+      implicit none
+      real(C_FLOAT),dimension(*),intent(out) :: sinc,space
+      integer(C_INT),value,intent(in) :: lsinc
+      real(C_FLOAT),value,intent(in) :: d
+    end subroutine
+  end interface
+
+contains
+
+  subroutine mksinc_table(nt,nsinc,table)
+    integer :: nt,nsinc,it;
+    real :: table(:,:),dtab,t,space(1000)
+
+    dtab=1.
+    dtab=1./nt
+    t=0
+    do it=1,nt
+    call mksincit(table(:,it),nsinc,t,space)
+    t=(it-1)*dtab
+    end do
+  end subroutine
+
+end module

### 2016-08-20 src/acoustic-2d-fortran/source_mod.f90

@@ -1,0 +1,93 @@
+module source_mod
+  use sep_mod
+  use sep
+  use modeling_mod
+  implicit none
+  type sourceT
+    real :: x,z
+    real  :: dt
+    real,allocatable :: dat(:)
+  end type
+  type Wavefield
+    real,allocatable :: ar(:,:)
+  end type
+  type sourceW
+     type(Wavefield), dimension(:),allocatable :: W
+  end type
+  contains
+  
+  
+  subroutine  initSourceSave(source,nb)
+    type(sourceW) :: source
+    integer :: nb
+    allocate(source%W(nb))
+ end subroutine
+ 
+ subroutine cleanSourceSave(source)
+   type(sourceW) :: source
+   integer :: i
+   do i=1,size(source%W)
+     deallocate(source%w(i)%ar)
+   end do
+   deallocate(source%w)
+  end subroutine
+  
+  subroutine setSourceLocation(source,loc)
+     type(sourceT) :: source
+     real :: loc
+     source%x=loc
+  end subroutine
+
+  
+  subroutine readSource(tag,src)
+   character(len=*) :: tag
+   type(sourceT) :: src
+   integer :: nt
+   real :: dt, ot
+   real, allocatable :: tmp(:)
+   character(len=128) :: tmpS
+   integer :: ierr
+ 
+
+   ierr= sep_get_data_axis_par(tag,1,nt,ot,dt,tmpS)
+
+   call from_param("src_z",src%z)
+   src%dt=dt
+
+   allocate(tmp(nt))
+   ierr=sreed(tag,tmp,size(tmp)*4)
+   allocate(src%dat(8+nt))
+   src%dat(1:4)=0
+   src%dat(5:4+nt)=tmp
+   src%dat(nt-3:)=0
+   deallocate(tmp)
+ end subroutine
+ 
+ 
+ subroutine addSource(src,tm,rnew,cur,scale)
+   type(sourceT) :: src
+   real :: tm
+   integer :: it,ix,iy,iz,ibase,isinc
+   real :: rnew(:,:)
+   real :: scale
+   type(modelingT) :: cur
+   real,pointer :: sincT(:)
+   it=tm/src%dt
+   isinc=(tm-it*src%dt)/src%dt*10000+1
+   sincT=>cur%sincT(:,isinc)
+   ibase=it+4
+   
+
+  if(ibase+7>size(src%dat)) return
[…]

### 2016-08-20 src/acoustic-2d-fortran/speedup.f90

@@ -1,0 +1,80 @@
+program  speedup
+  use sep
+  implicit none
+  integer :: n1,n2,n3
+  real :: d1,d2,d3,o1,o2,o3
+  integer :: nt,it
+  real :: tmax,tmin,errorFact
+  real :: dt,deltaT,vel,dist
+  real :: fmax,extent,qvalue,b(3),e(3),ff,cyclesKill,downfact
+  real :: dmax,dts,fkill,dsamp,base,aqx,aqy
+  real,allocatable :: cells(:,:)
+  integer :: nblocks,ierr,error,bound,i
+  logical :: follow
+
+  call sep_init()
+  call from_param("nblocks",nblocks,80)
+  
+  call from_param("nt",nt,2000)
+  call from_param("dt",dt,.004)
+  call from_param("vel",vel,2000.)
+  call from_param("error",error,10)
+  call from_param("bound",bound,20)
+  call from_param("downfact",downfact,.06)
+  call from_param("errorfact",errorfact,1.2)
+  
+  call from_param("fmax",fmax,70.)
+  call from_param("aqx",aqx,0.001)
+  call from_param("aqy",aqy,0.)
+  call from_param("extentxy",extent,13000.)
+  
+  
+  
+  
+  call from_param("qvalue",qvalue,50.)
+  call from_param("follow",follow,.true.)
+  deltaT=nt*dt/nblocks
+  tmin=0
+  ierr=sep_put_data_axis_par("out",1,nblocks,0.,deltaT,"time")
+  call to_history("n2",2)
+  b=(/0.,-extent,-extent/)
+  e=extent
+  allocate(cells(nblocks,2))
+  dmax=vel/fmax/2.8
+  dts=.49*dmax/vel
+  base=product((e-b)/dmax)*deltaT/dts
+  
+  
+  
+  
+  
+  do i=1,nblocks
+    tmax=tmin+deltaT
+    if(follow) then
+      dist=vel*tmax
+      b(2:3)=max(-extent,-dist);
+      e=(/min(extent,dist),min(dist+aqx,extent),min(dist+aqy,extent)/)
+    end if
+    ff=1.-2.*3.14159265/qvalue
+    cyclesKill=log(downfact)/log(ff)
+    fkill=cyclesKill/max(tmin,.001)
+    dsamp=max(dmax,vel/min(fmax,fkill)/2.8/errorFact)
[…]

### 2016-08-20 src/acoustic-2d-fortran/velmod.f90

@@ -1,0 +1,93 @@
+module vel_mod
+use resampleMod
+use modeling_mod
+use sep_mod
+use randomMod
+use sep
+implicit none
+real,private :: w0,qfact,gamma,pi
+type(modelingT) :: initialS
+type velT
+  integer :: n1,n2
+  real    :: o1,o2
+  real    :: d1,d2
+  real, allocatable, dimension(:,:) :: dat,vgamma
+end type
+contains
+
+subroutine readVel(fle,vel,full)
+  character(len=*)  :: fle
+  type(velT) :: vel
+  type(modelingT) :: full
+  character(len=128) :: junk
+  integer :: ierr
+  
+  ierr= sep_get_data_axis_par(fle,1,vel%n1,vel%o1,vel%d1,junk)
+  ierr= sep_get_data_axis_par(fle,2,vel%n2,vel%o2,vel%d2,junk)
+
+  call from_param("qfact",qfact,50.)
+  call from_param("w0",w0,60.)
+  pi=atan(1.)*4.
+  gamma=1./pi*atan(2*pi/qfact)
+ ! factor=(2.*pi*w0)**(-2.*gamma)
+  allocate(vel%dat(vel%n1,vel%n2))
+  ierr=sreed(fle,vel%dat,size(vel%dat)*4)
+  !vel%dat=1500
+  initialS%n1=vel%n1; initialS%o1=vel%o1; initialS%d1=vel%d1
+  initialS%n2=vel%n2; initialS%o2=vel%o2; initialS%d2=vel%d2
+  full%n1=vel%n1; full%o1=vel%o1; full%d1=vel%d1
+  full%n2=vel%n2; full%o2=vel%o2; full%d2=vel%d2
+end subroutine
+
+
+subroutine cleanVel(vel)
+  type(velT) :: vel
+  deallocate(vel%vgamma,vel%dat)
+end subroutine 
+
+subroutine resampleVel(vel,cur,vuse)
+  type(velT) :: vel,vuse
+  type(modelingT) :: cur
+  
+  deallocate(vuse%dat)
+
+ ! call setVelSize(vel,cur,vuse)
+  deallocate(vuse%vgamma)
+  allocate(vuse%dat(cur%n1,cur%n2))
+   allocate(vuse%vgamma(cur%n1,cur%n2))
+
+  call interpField(initialS,cur,vel%dat,vuse%dat,.true.)
+
[…]

### 2016-08-20 src/acoustic-3d-c/.ycm_extra_conf.py

@@ -1,0 +1,169 @@
+# This file is NOT licensed under the GPLv3, which is the license for the rest
+# of YouCompleteMe.
+#
+# Here's the license text for this file:
+#
+# This is free and unencumbered software released into the public domain.
+#
+# Anyone is free to copy, modify, publish, use, compile, sell, or
+# distribute this software, either in source code form or as a compiled
+# binary, for any purpose, commercial or non-commercial, and by any
+# means.
+#
+# In jurisdictions that recognize copyright laws, the author or authors
+# of this software dedicate any and all copyright interest in the
+# software to the public domain. We make this dedication for the benefit
+# of the public at large and to the detriment of our heirs and
+# successors. We intend this dedication to be an overt act of
+# relinquishment in perpetuity of all present and future rights to this
+# software under copyright law.
+#
+# THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
+# EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
+# MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT.
+# IN NO EVENT SHALL THE AUTHORS BE LIABLE FOR ANY CLAIM, DAMAGES OR
+# OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE,
+# ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR
+# OTHER DEALINGS IN THE SOFTWARE.
+#
+# For more information, please refer to <http://unlicense.org/>
+
+import os
+import ycm_core
+
+# These are the compilation flags that will be used in case there's no
+# compilation database set (by default, one is not set).
+# CHANGE THIS LIST OF FLAGS. YES, THIS IS THE DROID YOU HAVE BEEN LOOKING FOR.
+flags = [
+'-Wall',
+'-Wextra',
+'-Werror',
+'-Wno-long-long',
+'-Wno-variadic-macros',
+# THIS IS IMPORTANT! Without a "-std=<something>" flag, clang won't know which
+# language to use when compiling headers. So it will guess. Badly. So C++
+# headers will be compiled as C headers. You don't want that so ALWAYS specify
+# a "-std=<something>".
+# For a C project, you would set this to something like 'c99' instead of
+# 'c++11'.
+'-std=c++11',
[…]

### 2016-08-20 src/acoustic-3d-c/box.c

@@ -1,0 +1,261 @@
+#include <rsf.h>
+#include "box.h"
+
+static int   gs_timeblocks;
+static float gs_vmin;
+static float gs_vmax;
+static float gs_dmin;
+static float gs_dmax;
+static float gs_dtbig;
+static float gs_maxf; // maximum frequency
+static int   gs_nb; // boundary
+static float gs_error;
+static float gs_errorfact;
+static float gs_qfact;
+static float gs_downfact;
+static float gs_dt; /// read from wavelet file
+
+static float calgoodsampling(float dt) {
+  return 0.95 * dt;
+}
+
+static void find_exts(const int *ns, const float *os, const float *ds, float ***minT, float maxT, float *mymin, float *mymax)
+{
+  const int D = 3; // # of dimensions
+  for (int i = 0; i < D; i++) {
+    mymin[i] = os[i] + ns[i] * ds[i];
+    mymax[i] = os[i];
+  }
+
+  for (int i3 = 0; i3 < ns[2]; i3++) {
+    for (int i2 = 0; i2 < ns[1]; i2++) {
+      for (int i1 = 0; i1 < ns[0]; i1++) {
+        if (minT[i3][i2][i1] <= maxT) {
+          mymin[0] = fminf(mymin[0], os[0] + ds[0] * i1);
+          mymin[1] = fminf(mymin[1], os[1] + ds[1] * i2);
+          mymin[2] = fminf(mymin[2], os[2] + ds[2] * i3);
+          mymax[0] = fmaxf(mymax[0], os[0] + ds[0] * i1);
+          mymax[1] = fmaxf(mymax[1], os[1] + ds[1] * i2);
+          mymax[2] = fmaxf(mymax[2], os[2] + ds[2] * i3);
+        }
+      }
+    }
+  }
+}
+
+static void create_modeling(modeling_t *mod, const vel_t *vel, const times_t *times, float ***minT, float vmin, float vmax, float dmax, float maxf, float timemin, float timemax, float qfact, float downfact, float errorfact, float error, float *totallargecells, float *totalsmallcells)
+{
+  int   ns[3] = {times->n1, times->n2, times->n3};
+  float os[3] = {times->o1, times->o2, times->o3};
[…]

### 2016-08-20 src/acoustic-3d-c/box.h

@@ -1,0 +1,31 @@
+#ifndef BOX_H_MLWKBDTF
+#define BOX_H_MLWKBDTF
+
+#include <rsf.h>
+#include "vel.h"
+#include "model.h"
+
+typedef struct {
+  int n1, n2, n3, n4, n5;
+  float d1, d2, d3, d4, d5;
+  float o1, o2, o3, o4, o5;
+
+  float *****val;
+} times_t;
+
+
+typedef struct  {
+  int nt;
+  int totImaging;
+  float dt;
+  float blockSize;  // propagation time in each block
+  int timeblocks;
+  modeling_t *hyper;
+} box_t;
+
+times_t *read_times();
+
+box_t *calc_shot_box(const vel_t *vel, const times_t *times, const pt3d *src3d, const pt3d *rec3d, int nr, int nt, float dt);
+
+void init_box(int timeblocks, float vmin, float vmax, float dmin, float dmax, float maxf, int nb, float error, float errorfact, float qfact, float downfact, float dt);
+#endif /* end of include guard: BOX_H_MLWKBDTF */

### 2016-08-20 src/acoustic-3d-c/check.h

@@ -1,0 +1,12 @@
+#ifndef CHECK_H_NMIEIDTY
+#define CHECK_H_NMIEIDTY
+
+float fsum1(const float *a, int n);
+int isum1(const int *a, int n);
+void write3df(const char *file, float ***dat, int n1, int n2, int n3);
+void write2di(const char *file, int **dat, int n1, int n2);
+void write2df(const char *file, float **dat, int n1, int n2);
+void write1di(const char *file, int *dat, int n1);
+
+
+#endif /* end of include guard: CHECK_H_NMIEIDTY */

### 2016-08-20 src/acoustic-3d-c/common.c

@@ -1,0 +1,258 @@
+#include "common.h"
+
+
+
+#ifndef SF_HAS_SSE
+#undef __SSE__
+#endif
+#ifndef SF_HAS_AVX
+#undef __AVX__
+#endif
+
+#ifdef sun
+#define restrict
+#endif
+
+#if defined __SSE__ || defined __AVX__
+#include <immintrin.h>
+#endif
+
+
+  float*
+    damp_make(int ntransit)
+    {
+      int ib;
+      float* damp = NULL;
+      float sb, fb;
+      if (ntransit>0) damp = sf_floatalloc(ntransit);
+      sb = 4.0*ntransit;
+      for(ib=0; ib<ntransit; ib++) {
+        fb = ib/(sqrt(2.0)*sb);
+        damp[ib] = exp(-fb*fb);
+      }
+      return damp;
+    }
+
+  float*
+    compute_fdcoef(int nop, float dz, float dx, float dy, bool is_optimized, const int d_order)
+    /*
+       Optimized fd coeffifients from:
+       1. Yang Liu. "Globally optimal finite-difference schemes based on least squares" Geophysics 78.4 (2013)
+       2. Zhang, Jin-Hai, and Zhen-Xing Yao. "Optimized explicit finite-difference schemes for spatial derivatives using maximum norm." Journal of Computational Physics 250 (2013)
+
+       Conventional fd coefficients formula from:
+       3. Chunlei Chu, Paul Stoffa. "Determination of finite-difference weights using scaled binomial windows" Geophysics 77.3 (2012)
+       */
+    {
+      int idim, ii;
+#define ndim 3
+      float d2[ndim];
+      float d1[ndim];
+      float *d2_fdcoef;
+      float *ccc;
+      float *d1_fdcoef;
+      float *bbb;
+
+      d2[0] = dz*dz; d2[1] = dx*dx; d2[2] = dy*dy;
+      d1[0] = dz; d1[1] = dx; d1[2] = dy;
+
+      if (d_order == 2) {
+        d2_fdcoef = sf_floatalloc(ndim*nop+1);
+        if (is_optimized) ccc= optimal_fdcoef(nop,2);
+        else ccc = normal_fdcoef(nop,d_order);
+
[…]

### 2016-08-20 src/acoustic-3d-c/fdutil.h

@@ -1,0 +1,672 @@
+/* This file is automatically generated. DO NOT EDIT! */
+
+#ifndef _fdutil_h
+#define _fdutil_h
+
+
+typedef struct fdm2 *fdm2d;
+
+
+typedef struct fdm3 *fdm3d;
+
+
+typedef struct scoef2 *scoef2d;
+
+
+typedef struct scoef3 *scoef3d;
+
+
+typedef struct lcoef2 *lint2d;
+
+
+typedef struct lcoef3 *lint3d;
+
+
+typedef struct abc2 *abcone2d;
+
+
+typedef struct abc3 *abcone3d;
+
+
+typedef struct spon *sponge;
+
+
+typedef struct ofg *ofg2d;
+
+
+typedef struct PML2D *PML2D;
+
+
+typedef struct PML3D *PML3D;
+
+
+struct fdm2{
+  int nb;
+  int   nz,nzpad;
+  int   nx,nxpad;
+  float oz,ozpad;
+  float ox,oxpad;
+  float dz;
+  float dx;
+  bool verb;
+  bool free;
+  int ompchunk;
+};
+
+
+struct fdm3{
+  int nb;
+  int   nz,nzpad;
+  int   nx,nxpad;
+  int   ny,nypad;
+  float oz,ozpad;
+  float ox,oxpad;
+  float oy,oypad;
+  float dz;
+  float dx;
+  float dy;
+  bool verb;
+  bool free;
+  int ompchunk;
+};
+
+
+struct scoef2{
+  int n;
+  int ix,iz;
+  int fx,fz,nx,nz;
+  float sincx[9], sincz[9];
+};
+
+
+struct scoef3{
+  int n;
+  int iy,ix,iz;
+  int fy,fx,fz,ny,nx,nz;
+  float sincy[9],sincx[9], sincz[9];
+};
+
+
+struct lcoef2{
+  int n;
+  float *w00;
+  float *w01;
+  float *w10;
+  float *w11;
+  int *jz;
+  int *jx;
+};
+
+
+struct lcoef3{
+  int n;
+  float *w000;
+  float *w001;
+  float *w010;
+  float *w011;
+  float *w100;
+  float *w101;
+  float *w110;
+  float *w111;
+  int *jz;
+  int *jx;
+  int *jy;
+};
+
+
+struct abc2{
+  bool free;
+  float *bzl;
+  float *bzh;
+  float *bxl;
+  float *bxh;
+};
+
+
+struct abc3{
+  bool free;
+  float**bzl;
[…]

### 2016-08-20 src/acoustic-3d-c/main-fd3d.c

@@ -1,0 +1,415 @@
+#include <rsf.h>
+#include <assert.h>
+#include "fdutil.h"
+#include "common.h"
+#include "step-forward.h"
+#include "box.h"
+#include "check.h"
+#include "vel.h"
+#include "resample.h"
+
+fdm3d mkfdm(bool verb, bool fsrf, const modeling_t *m)
+{
+  int nbd = m->nb;
+  sf_axis az = sf_maxa(m->n1 - 2 * m->nb, m->o1 + nbd * m->d1, m->d1);
+  sf_axis ax = sf_maxa(m->n2 - 2 * m->nb, m->o2 + nbd * m->d2, m->d2);
+  sf_axis ay = sf_maxa(m->n3 - 2 * m->nb, m->o3 + nbd * m->d3, m->d3);
+
+  return fdutil3d_init(verb,fsrf,az,ax,ay,nbd,1);
+}
+
+int main(int argc, char** argv)
+{
+
+  bool verb, fsrf, snap, expl, dabc, cden, adj;
+  bool optfd, hybrid, sinc;
+  int jsnap, jdata;
+
+  /* I/O files */
+  sf_file file_wav=NULL; /* wavelet */
+  sf_file file_vel=NULL; /* velocity */
+  sf_file file_den=NULL; /* density */
+  sf_file file_wfl=NULL; /* wavefield */
+  sf_file file_dat=NULL; /* data */
+  sf_file file_src=NULL; /* sources */
+  sf_file file_rec=NULL; /* receivers */
+
+  /* cube axes */
+  sf_axis at = NULL, az = NULL, ax = NULL, ay = NULL;
+  sf_axis as = NULL, ar = NULL;
+
+  int nbd;  /* ABC boundary size */
+  int fdorder;  /* finite difference spatial accuracy order */
+  int nzpad,nxpad,nypad; /* boundary padded model size */
+  int ix,iy,it,nx,ny,nz,nt,ns,nr;
+  float ox,oy,oz,dx,dy,dz,dt,dt2;
+  float* damp=NULL; /* damping profile for hybrid bc */
+  float* ws;  /* wavelet */
+  float*** vel=NULL;  /* velocity */
+  float*** rho=NULL; /* density */
+  float*** u0=NULL;  /* wavefield array u@t-1 (u@t+1) */
+  float*** u1=NULL;  /* wavefield array u@t */
[…]

### 2016-08-20 src/acoustic-3d-c/model.h

@@ -1,0 +1,13 @@
+#ifndef MODEL_H_CCD6OOYW
+#define MODEL_H_CCD6OOYW
+
+typedef struct {
+  int n1, n2, n3;
+  float o1, o2, o3;
+  float d1, d2, d3;
+  int nb;
+  float dt, dtextra;
+  int ntblock;
+} modeling_t;
+
+#endif /* end of include guard: MODEL_H_CCD6OOYW */

### 2016-08-20 src/acoustic-3d-c/resample.c

@@ -1,0 +1,307 @@
+#include "resample.h"
+#include "check.h"
+#include <assert.h>
+
+static int gs_ns;
+static int gs_npts;
+static float **gs_sinc_table;
+
+/************************************************************************
+*                          Subroutine toep                              *
+*************************************************************************
+*                 Toeplitz system solver: solves rf=g                   *
+*************************************************************************
+*/
+static void toep (int m, const float *r,float *f,float *g,float *a){
+  int i,j,jh;
+  double c,e,v,w,bot;
+
+  a[0]=1.;
+  v=r[0];
+  f[0]=g[0]/r[0];
+
+  for (j=1; j<m; j++) {
+
+    /* solve ra=v as in Claerbout, FGDP, p. 57 */
+    e = a[j] = f[j] = 0.;
+    for (i=0; i<j; i++)
+    e += a[i]*r[j-i];
+    c = e/v;
+    v -= e*c;
+    jh = j/2;
+    for (i=0; i<=jh; i++) {
+      bot = a[j-i]-c*a[i];
+      a[i] -= c*a[j-i];
+      a[j-i] = bot;
+    }
+
+    /* use a and v above to get f[i], i = 0,1,2,...,j */
+    w = 0;
+    for (i=0; i<j; i++)
+      w += f[i]*r[j-i];
+    c = (g[j]-w)/v;
+    for (i=0; i<=j; i++)
+      f[i] += c*a[j-i];
+  }
+}
+
+/************************************************************************
+*                          Subroutine mksinc                            *
+*************************************************************************
+* Derives tapered sinc interpolator coefficients by least squares       *
+* spectral matching.  Theory in WGC technical document by Larner, 1979. *
+*  Dave Hale, 1/31/83                                                   *
+*************************************************************************
+*   sinc    tapered sinc interpolation coefficients                     *
[…]

### 2016-08-20 src/acoustic-3d-c/resample.h

@@ -1,0 +1,10 @@
+#ifndef RESAMPLE_H_WQCWR39E
+#define RESAMPLE_H_WQCWR39E
+
+#include "model.h"
+#include <rsf.h>
+
+void init_sinc_table(int nsinc, int npts);
+void interpfield(const modeling_t *olds, const modeling_t *news, float ***oldf, float ***newf, bool extend);
+
+#endif /* end of include guard: RESAMPLE_H_WQCWR39E */

### 2016-08-20 src/acoustic-3d-c/sinc.c

@@ -1,0 +1,94 @@
+#include<math.h>
+#include<stdio.h>
+void mksinc (float *sinc,int lsinc,float d,float *space);;
+void toep (int m,float *r,float *f,float *g,float *a);
+
+/************************************************************************
+*                          Subroutine mksinc                            *
+*************************************************************************
+* Derives tapered sinc interpolator coefficients by least squares       *
+* spectral matching.  Theory in WGC technical document by Larner, 1979. *
+*  Dave Hale, 1/31/83                                                   *
+************************************************************************* 
+*   sinc    tapered sinc interpolation coefficients                     *
+*   lsinc   length of sinc -- MUST BE EVEN; lsinc<20 RECOMMENDED!       *
+*   d       fractional distance to interpolated point; 0<=d<=1 REQUIRED!*
+*   space   workspace of lsinc*3 floats                                 * 
+*************************************************************************
+*After calling mksinc, use the coefficients to interpolate as follows:  *
+*                    j=lsinc-1                                          *
+* y(t) = y(i+d) =      sum     sinc[j]*y[i+j-lsinc/2+1]                 *
+*                      j=0                                              *
+************************************************************************/
+void mksincit (float *sinc,int lsinc,float d,float *space)
+  {
+	int j;
+	float *b,*c,*work,pi,pi2,snyq,snat,s0,ds,eta,s;
+
+	/* compute constants */
+	pi = 3.141592654;
+	pi2 = pi*2;
+	snyq = 0.5;
+	snat = snyq*(0.066+0.265*log((double)lsinc));
+	s0 = 0.0;
+	ds = (snat-s0)/(lsinc*2-1);
+	eta = lsinc/2-1.0+d;
+
+	/* segment work space */
+	b = space; c = b+lsinc; work = c+lsinc;
+
+	/* compute coefficients of Toeplitz linear system */
+	for (j=0; j<lsinc; j++){
+		for (s=s0,b[j]=c[j]=0.0; s<=snat; s+=ds)
+		  {
+			b[j] += cos(pi2*s*j);
+			c[j] += cos(pi2*s*(eta-j));
+		  }
+	}
+
+	/* solve the system for sinc coefficients */
+	toep (lsinc,b,sinc,c,work);
+
+}
+
+
[…]

### 2016-08-20 src/acoustic-3d-c/step-forward.c

@@ -1,0 +1,275 @@
+#include "step-forward.h"
+
+#include <rsf.h>
+
+#ifdef _OPENMP
+#include <omp.h>
+#else
+#include <time.h>
+#endif
+
+#ifndef SF_HAS_SSE
+#undef __SSE__
+#endif
+#ifndef SF_HAS_AVX
+#undef __AVX__
+#endif
+
+#ifdef sun
+#define restrict
+#endif
+
+#if defined __SSE__ || defined __AVX__
+#include <immintrin.h>
+#endif
+void step_forward(float*** restrict u0, float*** restrict u1,
+    float*** restrict vel, float*** restrict rho,
+    float* restrict fdcoef_d2, float* restrict fdcoef_d1,
+    int nop, int nzpad, int nxpad, int nypad)
+{
+  int ix, iy, iz, iop;
+  float c0 = fdcoef_d2[0];
+  float *cz = &fdcoef_d2[0];
+  float *cx = &fdcoef_d2[nop];
+  float *cy = &fdcoef_d2[nop+nop];
+  float *bz, *bx, *by;
+  float drho_dot_du;
+  float du_z = 0.f, du_x = 0.f, du_y = 0.f;
+  float drho_z = 0.f, drho_x = 0.f, drho_y = 0.f;
+  float lap;
+
+  if (rho != NULL) { /* variable density */
+    bz = &fdcoef_d1[0];
+    bx = &fdcoef_d1[nop];
+    by = &fdcoef_d1[nop+nop];
+  }
+
+#ifdef __SSE__
+#define vType __m128
+#define _prefix_loadu_ps _mm_loadu_ps
+#define _prefix_storeu_ps _mm_storeu_ps
+#define _prefix_add_ps _mm_add_ps
+#define _prefix_sub_ps _mm_sub_ps
+#define _prefix_mul_ps _mm_mul_ps
+#define _prefix_div_ps _mm_div_ps
+#define _prefix_set1_ps _mm_set1_ps
+#elif defined __AVX__
+#define vType __m256
+#define _prefix_loadu_ps _mm256_loadu_ps
+#define _prefix_storeu_ps _mm256_storeu_ps
+#define _prefix_add_ps _mm256_add_ps
+#define _prefix_sub_ps _mm256_sub_ps
+#define _prefix_mul_ps _mm256_mul_ps
+#define _prefix_div_ps _mm256_div_ps
[…]

### 2016-08-20 src/acoustic-3d-c/step-forward.h

@@ -1,0 +1,14 @@
+#ifndef STEP_FORWARD_H_PL2PUYAU
+#define STEP_FORWARD_H_PL2PUYAU
+
+void step_forward(float*** restrict u0, float*** restrict u1,
+    float*** restrict vel, float*** restrict rho,
+    float* restrict fdcoef_d2, float* restrict fdcoef_d1,
+    int nop, int nzpad, int nxpad, int nypad);
+
+void step_forward_q(float*** restrict u0, float*** restrict u1,
+    float*** restrict vel, float *** restrict vgamma, float*** restrict rho,
+    float* restrict fdcoef_d2, float* restrict fdcoef_d1,
+    int nop, int nzpad, int nxpad, int nypad);
+
+#endif /* end of include guard: STEP_FORWARD_H_PL2PUYAU */

### 2016-08-20 src/acoustic-3d-c/test1.c

@@ -1,0 +1,425 @@
+#include <rsf.h>
+#include "fdutil.h"
+#include "common.h"
+#include "step-forward.h"
+#include "box.h"
+#include "check.h"
+#include "vel.h"
+#include "resample.h"
+
+int main(int argc, char** argv)
+{
+
+  bool verb, fsrf, snap, expl, dabc, cden, adj;
+  bool optfd, hybrid, sinc;
+  int jsnap, jdata;
+
+  /* I/O files */
+  sf_file file_wav=NULL; /* wavelet */
+  sf_file file_vel=NULL; /* velocity */
+  sf_file file_den=NULL; /* density */
+  sf_file file_wfl=NULL; /* wavefield */
+  sf_file file_dat=NULL; /* data */
+  sf_file file_src=NULL; /* sources */
+  sf_file file_rec=NULL; /* receivers */
+
+  /* cube axes */
+  sf_axis at = NULL, az = NULL, ax = NULL, ay = NULL;
+  sf_axis as = NULL, ar = NULL;
+
+  int nbd;  /* ABC boundary size */
+  int fdorder;  /* finite difference spatial accuracy order */
+  int nzpad,nxpad,nypad; /* boundary padded model size */
+  int ix,iy,it,nx,ny,nz,nt,ns,nr;
+  float ox,oy,oz,dx,dy,dz,dt,dt2;
+  float* damp=NULL; /* damping profile for hybrid bc */
+  float* ws;  /* wavelet */
+  float*** vel=NULL;  /* velocity */
+  float*** rho=NULL; /* density */
+  float*** u0=NULL;  /* wavefield array u@t-1 (u@t+1) */
+  float*** u1=NULL;  /* wavefield array u@t */
+  float* u_dat=NULL; /* output data */
+  float*** ptr_tmp=NULL;
+  pt3d* src3d=NULL;  /* source position */
+  pt3d* rec3d=NULL;  /*receiver position*/
+  scoef3d cssinc = NULL, crsinc = NULL;
+  lint3d cslint = NULL, crlint = NULL;
+
+  /* FDM structure */
+  fdm3d fdm = NULL;
+  abcone3d abc = NULL;
+  sponge spo = NULL;
+
+  float* fdcoef_d2;
+  float* fdcoef_d1;
+
[…]

### 2016-08-20 src/acoustic-3d-c/vel.c

@@ -1,0 +1,106 @@
+#include "vel.h"
+#include "resample.h"
+
+#include <rsf.h>
+
+static float gs_w0;
+static float gs_qfact;
+static float gs_gamma;
+
+modeling_t make_modeling(const vel_t *v)
+{
+  modeling_t m;
+  m.n1 = v->n1; m.o1 = v->o1; m.d1 = v->d1;
+  m.n2 = v->n2; m.o2 = v->o2; m.d2 = v->d2;
+  m.n3 = v->n3; m.o3 = v->o3; m.d3 = v->d3;
+
+  return m;
+}
+
+vel_t *read_vel(const char *tag)
+{
+  sf_file fvel = sf_input(tag);
+  sf_seek(fvel, 0, SEEK_SET);
+
+  vel_t *v = malloc(sizeof *v);
+  sf_histint(fvel, "n1", &v->n1);
+  sf_histint(fvel, "n2", &v->n2);
+  sf_histint(fvel, "n3", &v->n3);
+  sf_histfloat(fvel, "o1", &v->o1);
+  sf_histfloat(fvel, "o2", &v->o2);
+  sf_histfloat(fvel, "o3", &v->o3);
+  sf_histfloat(fvel, "d1", &v->d1);
+  sf_histfloat(fvel, "d2", &v->d2);
+  sf_histfloat(fvel, "d3", &v->d3);
+
+  v->dat = sf_floatalloc3(v->n1, v->n2, v->n3);
+  sf_floatread(v->dat[0][0], v->n1 * v->n2 * v->n3, fvel);
+
+  return v;
+}
+
+vel_t *clone_vel(float ***vel, int nz, int nx, int ny,
+    float oz, float ox, float oy,
+    float dz, float dx, float dy,
+    float w0, float qfact)
+{
+  vel_t *v = malloc(sizeof *v);
+  v->n1 = nz; v->n2 = nx; v->n3 = ny;
+  v->o1 = oz; v->o2 = ox; v->o3 = oy;
+  v->d1 = dz; v->d2 = dx; v->d3 = dy;
+  v->dat = sf_floatalloc3(nz, nx, ny);
+  memcpy(v->dat[0][0], vel[0][0], nz*nx*ny*sizeof(float));
+  v->vgamma = sf_floatalloc3(1,1,1);
+
+  gs_w0 = w0; gs_qfact= qfact;
[…]

### 2016-08-20 src/acoustic-3d-c/vel.h

@@ -1,0 +1,26 @@
+#ifndef VEL_H_BLY3XMED
+#define VEL_H_BLY3XMED
+
+#include "model.h"
+
+typedef struct {
+  int   n1, n2, n3;
+  float o1, o2, o3;
+  float d1, d2, d3;
+  float ***dat;
+  float ***vgamma;
+} vel_t;
+
+void vmin_vmax_dmin_dmax(const vel_t *vel, float *vmin, float *vmax, float *dmin, float *dmax);
+
+vel_t *clone_vel(float ***vel, int nz, int nx, int ny,
+    float oz, float ox, float oy,
+    float dz, float dx, float dy,
+    float w0, float qfact);
+
+vel_t *read_vel(const char *tag);
+modeling_t make_modeling(const vel_t *v);
+void resample_vel(const modeling_t *olds, const modeling_t *news, const vel_t *oldv, vel_t *newv);
+void resample_p(const modeling_t *olds, const modeling_t *news, float ****p);
+
+#endif /* end of include guard: VEL_H_BLY3XMED */

### 2016-08-20 src/acoustic-3d-fortran/box_mod.f90

@@ -1,0 +1,428 @@
+module box_mod
+  use sinc_mod
+  use modeling_mod
+  use sep
+  use vel_mod
+  use data_mod
+  use source_mod
+  implicit none
+  logical, private :: v
+  real, private :: vmin,vmax,dmin,dmax
+  double precision :: tot1Cells,tot2Cells
+  integer :: totImaging
+  integer,private :: timeBlocks
+  real,private :: dstable
+  integer :: slow
+  integer, private :: bound,error,jimage
+  real,private :: errorFact,downFact,qfact,maxF,dtBig
+  real, pointer :: sincT(:,:)
+
+  type timesT
+    integer :: n1,n2,n3,n4,n5
+    real    :: o1,o2,o3,o4,o5
+    real    :: d1,d2,d3,d4,d5
+    real,allocatable :: vals(:,:,:,:,:)
+  end type
+
+  type boxT
+    type(modelingT), pointer :: hyper(:)
+    integer :: nt
+    real    :: dt
+    integer :: totImaging
+    real :: blockSize
+
+  end type
+
+  !interface
+  !subroutine fastmarch(order,s1,s2,s3,b1,b2,b3,n1,n2,n3,d1,d2,d3,s0,slow,ttime) bind(c,name="fastmarch")
+  !import
+  !real(c_float),intent(in),value:: s1,s2,s3,d1,d2,d3,s0
+  !integer(c_int), value,intent(in) :: order,b1,b2,b3,n1,n2,n3
+  !real(c_float),dimension(*) :: slow,ttime
+  !end subroutine
+  !end interface
+
+contains
+
+  subroutine initTimes(timesS)
+    type(timesT) :: timesS
+    integer :: ierr
+    character(len=128) :: label
+    ierr=sep_get_data_axis_par("times",1,timesS%n1,timesS%o1,timesS%d1,label)
+    ierr=sep_get_data_axis_par("times",2,timesS%n2,timesS%o2,timesS%d2,label)
+    ierr=sep_get_data_axis_par("times",3,timesS%n3,timesS%o3,timesS%d3,label)
+    ierr=sep_get_data_axis_par("times",4,timesS%n4,timesS%o4,timesS%d4,label)
+    ierr=sep_get_data_axis_par("times",5,timesS%n5,timesS%o5,timesS%d5,label)
[…]

### 2016-08-20 src/acoustic-3d-fortran/data_mod.f90

@@ -1,0 +1,128 @@
+module data_mod
+  use modeling_mod
+  use sep_mod
+  use sep
+  implicit none
+
+  type dataT
+    integer :: n1,n2,n3,n4,n5
+    real :: o1,o2,o3,o4,o5
+    real :: d1,d2,d3,d4,d5
+    real :: depth
+    real,allocatable :: dat(:,:,:)
+    real,allocatable :: floc(:,:,:)
+    character(len=128) :: tag
+  end type
+
+contains
+
+  subroutine initData(tag,dat)
+    character(len=*) :: tag
+    type(dataT) :: dat
+    integer :: ierr
+    character(len=120) :: tmpS
+
+    ierr= sep_get_data_axis_par(tag,1,dat%n1,dat%o1,dat%d1,tmpS)
+    ierr= sep_get_data_axis_par(tag,2,dat%n2,dat%o2,dat%d2,tmpS)
+    ierr= sep_get_data_axis_par(tag,3,dat%n3,dat%o3,dat%d3,tmpS)
+    ierr= sep_get_data_axis_par(tag,4,dat%n4,dat%o4,dat%d4,tmpS)
+    ierr= sep_get_data_axis_par(tag,5,dat%n5,dat%o5,dat%d5,tmpS)
+    dat%tag=tag
+
+    call from_param("depth",dat%depth,0.)
+    allocate(dat%floc(3,dat%n2,dat%n3)) !ASK: right?
+    allocate(dat%dat(dat%n1+10,dat%n2,dat%n3)) ! ASK: why n1+10, not both n1,n2
+
+  end subroutine
+
+
+  function getShotLocation(dat,ishot) result(res)
+    type(dataT) :: dat
+    integer :: ishot(:)
+    integer :: sx, sy
+    real :: res(2)
+
+    sx = dat%o4 + dat%d4*(ishot(1)-1)
+    sy = dat%o5 + dat%d5*(ishot(2)-1)
+
+    res = (/sx, sy/)
+    !res=dat%o3+dat%d3*(ishot-1)
+
+  end function
+
+  subroutine readShot(dat,ishot)
+    type(dataT) :: dat
+    integer :: ishot(:)
+    integer :: ixshot, iyshot
+    integer :: ierr,i2, i3
+    real :: x, y
[…]

### 2016-08-20 src/acoustic-3d-fortran/image_mod.f90

@@ -1,0 +1,122 @@
+module image_mod
+  !use resampleMod
+  use modeling_mod
+  use vel_mod
+  implicit none
+  real, allocatable,private :: imageTot(:,:,:)
+  type(modelingT),private :: myD
+  type imageT
+    integer :: n1,n2,n3,n4
+    real    :: o1,o2,o3,o4
+    real    :: d1,d2,d3,d4
+    real, allocatable, dimension(:,:,:) :: dat
+  end type
+
+contains
+
+  subroutine calcImage(vel,tag)
+    type(velT) :: vel
+    character(len=*) tag
+    integer :: ierr
+    ierr= sep_put_data_axis_par(tag,1,vel%n1,vel%o1,vel%d1,"Z")
+    ierr= sep_put_data_axis_par(tag,2,vel%n2,vel%o2,vel%d2,"X")
+    ierr= sep_put_data_axis_par(tag,3,vel%n2,vel%o2,vel%d2,"Y")
+
+    allocate(imageTot(vel%n1,vel%n2,vel%n3))
+    imageTot=0
+    myD%n1=vel%n1; myd%o1=vel%o1; myd%d1=vel%d1
+    myD%n2=vel%n2; myd%o2=vel%o2; myd%d2=vel%d2
+    myD%n3=vel%n3; myd%o3=vel%o3; myd%d3=vel%d3
+
+
+  end subroutine
+
+  subroutine cleanIuse(iuse)
+    type(imageT) :: iuse
+    deallocate(iuse%dat)
+  end subroutine
+
+  subroutine createIuse(cur,iuse)
+  type(modelingT) :: cur
+  type(imageT) :: iuse
+
+  iuse%n1=cur%n1; iuse%o1=cur%o1; iuse%d1=cur%d1
+  iuse%n2=cur%n2; iuse%o2=cur%o2; iuse%d2=cur%d2
+  iuse%n3=cur%n3; iuse%o3=cur%o3; iuse%d3=cur%d3
+
+  allocate(iuse%dat(iuse%n1,iuse%n2,iuse%n3))
+  iuse%dat=0
+  end subroutine
+
+  subroutine resampleI(iuse,old,cur)
+  type(modelingT) :: old,cur
+  type(imageT) :: iuse
+  real, allocatable :: tmp(:,:,:)
+  integer :: ierr
+  allocate(tmp(myd%n1,myd%n2,myd%n3))
+  call InterpField(old,myD,iuse%dat,tmp,.false.)
[…]

### 2016-08-20 src/acoustic-3d-fortran/main.f90

@@ -1,0 +1,1 @@
+main_old.f90

### 2016-08-20 src/acoustic-3d-fortran/mainInterp.f90

@@ -1,0 +1,37 @@
+program RTM_FAST
+  use my_timers_mod
+  use vel_mod
+  use data_mod
+  use image_mod
+  use source_mod
+  use box_mod
+  use migrate_shot_mod
+  use sep
+  logical :: verb
+  type(velT) :: vel, bigVel
+  type(timesT) :: times
+  type(sourceT) :: source
+  type(dataT)   :: dat
+  type(modelingT) :: small,full
+  integer :: ishot,ii
+  real :: factor,rnd
+  integer, allocatable :: shot(:, :, :) ! first dimension store the real index
+  logical, allocatable :: shotL(:, :)
+
+
+  call initpar()
+  call setup_timers()
+
+  call readVel("vel", vel, small)
+  call readVel("vel2", bigVel, full)
+  bigVel%dat = 0
+  call init_sinc_table(8, 10000)
+
+  call interpField(small, full, vel%dat, bigVel%dat, .true.)
+
+  ii = sep_put_data_axis_par('c.H', 1, full%n1, full%o1, full%d1, "Z")
+  ii = sep_put_data_axis_par('c.H', 2, full%n2, full%o2, full%d2, "X")
+  ii = sep_put_data_axis_par('c.H', 3, full%n3, full%o3, full%d3, "Y")
+  ii = srite('c.H', bigVel%dat, size(bigVel%dat)*4)
+  write(0,*) 'program exit normally'
+end program

### 2016-08-20 src/acoustic-3d-fortran/main_old.f90

@@ -1,0 +1,70 @@
+program RTM_FAST
+  use my_timers_mod
+  use vel_mod
+  use data_mod
+  use image_mod
+  use source_mod
+  use box_mod
+  use migrate_shot_mod
+  use sep
+  logical :: verb
+  type(velT) :: vel
+  type(timesT) :: times
+  type(sourceT) :: source
+  type(dataT)   :: dat
+  type(modelingT) :: full
+  integer :: ishot,ii
+  real :: factor,rnd
+  integer, allocatable :: shot(:, :, :) ! first dimension store the real index
+  logical, allocatable :: shotL(:, :)
+
+
+  call initpar()
+  call setup_timers()
+
+  !SETUP global migration parameters
+  call start_timer_num(timerInit)
+  call from_param("verbose",verb,.false.)
+  call readVel("vel",vel,full)
+  call initData("data",dat)
+  call calcImage(vel,"img")
+  call readSource("source",source)
+  call initTimes(times)
+  call initBox(dat,source,vel,verb)
+
+  call init_sinc_table(8,10000)
+  call stop_timer_num(timerInit)
+
+
+  allocate(shot(2, dat%n4, dat%n5), shotL(dat%n4, dat%n5))
+  shotL=.false.
+
+  write(0,*) 'dat%n4',dat%n4, ' dat%n5', dat%n5
+
+  ! ASK: what's doing in 2D cases?
+  iyshot=1
+  do while(iyshot<= dat%n5)
+    ixshot = 1
+    do while(ixshot<= dat%n4)
+      call random_number(rnd)
+      ii=max(1,min(dat%n4,nint(rnd*dat%n4)+1))
+      jj=max(1,min(dat%n5,nint(rnd*dat%n5)+1))
+      if(.not. shotL(ii, jj)) then
+        shot(:,ixshot, iyshot)=(/ii, jj/)
+        ixshot = ixshot + 1
+      end if
+    end do
+    iyshot = iyshot + 1
+  end do
+
+  do iyshot = 1, dat%n5
+    do ixshot = 1, dat%n4
+      factor= migrate_shot(shot(:, ixshot, iyshot),verb,vel,dat,source,times)
+      write(0,*) ixshot, " MIGRATING SHOT", shot(1, ixshot, iyshot), " of ",dat%n4, " sped up ",factor
+      !if(mod(ishot,5)==0)  call writeFullImage("img")
+    end do
+  end do
+  call print_timers()
+  call writeFullImage("img")
+
+end program

### 2016-08-20 src/acoustic-3d-fortran/make_time.f90

@@ -1,0 +1,51 @@
+module times_mod
+use iso_c_binding
+interface
+   subroutine fastmarch(order,s1,s2,s3,b1,b2,b3,n1,n2,n3,d1,d2,d3,s0,slow,ttime) bind(c,name="fastmarch")
+     import
+     real(c_float),intent(in),value:: s1,s2,s3,d1,d2,d3,s0
+     integer(c_int), value,intent(in) :: order,b1,b2,b3,n1,n2,n3
+     real(c_float),dimension(*) :: slow,ttime
+    end subroutine
+ end interface
+end module
+
+program ttimes
+use times_mod
+use sep
+implicit none
+integer :: n1,n2,n3
+real :: o1,o2,o3
+real :: d1,d2,d3
+integer :: ierr
+integer :: j2,j3,i3,i2,n4out,n5out
+character(len=128) :: junk
+real,allocatable :: times(:,:,:),vel(:,:,:)
+real :: s1,s2,s3,s0
+
+call sep_init()
+call from_param("j2",j2,1)
+call from_param("j3",j3,1)
+ierr=sep_get_data_axis_par("in",1,n1,o1,d1,junk)
+ierr=sep_get_data_axis_par("in",2,n2,o2,d2,junk)
+ierr=sep_get_data_axis_par("in",3,n3,o3,d3,junk)
+n4out=ceiling(real(n2)/real(j2))
+n5out=ceiling(real(n3)/real(j3))
+ierr=sep_put_data_axis_par("out",4,n4out,o2,d2*j2,"x position")
+ierr=sep_put_data_axis_par("out",5,n5out,o3,d3*j3,"y position")
+allocate(vel(n1,n2,n3),times(n1,n2,n3))
+ierr=sreed("in",vel,size(vel)*4)
+vel=1./vel
+s1=0
+
+do i3=1,n3,j3
+  do i2=1,n2,j2
+    write(0,*) "working on shot (",(i2-1)/j2+1,(i3-1)/j3+1, ") of (",n4out,n5out,")"
+    s2=(i2-1)*d2
+    s3=(i3-1)*d3
+    s0=vel(1,i2,i3)
+    call fastmarch(3,s1,s2,s3,1,1,1,n1,n2,n3,d1,d2,d3,s0,vel,times)
+    ierr=srite("out",times,size(times)*4)
+  end do
+end do
+end program

### 2016-08-20 src/acoustic-3d-fortran/mig_shot.f90

@@ -1,0 +1,271 @@
+module migrate_shot_mod
+  use sep
+  use vel_mod
+  use prop_mod
+  use my_timers_mod
+  use image_mod
+  use box_mod
+  use data_mod
+  use source_mod
+  implicit none
+  logical, private :: qtest
+  integer,private  :: writeSection,icount, waveFieldWriteCnt
+  integer, private :: writeCheckPoint
+
+
+
+contains
+
+
+real function migrate_shot(ishot,verb,vel,dat,source,times) result(factor)
+  integer :: ishot(:)
+  logical :: verb
+  type(velT) :: vel,vuse
+  type(dataT) :: dat
+  type(sourceT) :: source
+  type(timesT)  :: times
+  type(imageT) :: iuse
+  type(boxT)  :: domain
+  type(waveT), target :: p1,p2,p3
+  type(waveT), pointer :: pold,pcur,pnew
+  type(modelingT),pointer :: cur,old
+  type(modelingT) :: full
+  type(sourceW) :: sou
+  integer :: iblock,it,iimage,slow,ierr
+  logical :: xx
+  real :: t0
+
+  waveFieldWriteCnt = 0
+
+  full%o1=vel%o1; full%d2=vel%d2 ;full%n2=vel%n2;
+  full%o2=vel%o2; full%d1=vel%d1; full%n1=vel%n1
+  full%o3=vel%o3; full%d3=vel%d3; full%n3=vel%n3
+  call start_timer_num(timerIS)
+  call readShot(dat,ishot)
+  call setSourceLocation(source,getShotLocation(dat,ishot))
+  call from_param("qtest",qtest,.false.)
+  call from_param("writeSection",writeSection,-1)
+  call from_param("writeCheckpoint",writeCheckpoint,-1)
+  icount=0
+  factor=calcShotBox(vel,dat,source,times,domain)
+  cur=>domain%hyper(1); old=>cur
+  if(writeCheckPoint>0) then
+    ierr= sep_put_data_axis_par("wfield",1,vel%n1,vel%o1,vel%d1,"Depth");
+    ierr= sep_put_data_axis_par("wfield",2,vel%n2,vel%o2,vel%d2,"X Position");
+    ierr= sep_put_data_axis_par("wfield",3,vel%n3,vel%o3,vel%d3,"Y Position");
+  end if
+
+  call initWavefields(cur,p1,p2,p3)
[…]

### 2016-08-20 src/acoustic-3d-fortran/modeling_mod.f90

@@ -1,0 +1,44 @@
+module modeling_mod
+implicit none
+type modelingT
+  real,pointer :: sincT(:,:) ! ASK: what's sincT mean
+  integer :: oversamp,oversampS
+  real :: o1,o2,o3
+  integer :: n1,n2,n3
+  real :: d1,d2,d3
+  integer :: bnd
+  integer,allocatable :: b(:,:), e(:,:)
+  integer :: b1,b2,b3,nsect
+  double precision :: d1a(5),d2a(5),d3a(5)
+  real :: d0,dt,dtextra
+  integer :: ntblock
+  integer :: jimage
+end type
+
+
+contains
+
+logical function checkSame(a,b) result(res)
+  type(modelingT) :: a,b
+  real :: d
+
+  res=.false.
+  if(a%n1/=b%n1 .or. a%n2/=b%n2 .or. a%n3/=b%n3) then
+     return
+  end if
+  if(abs(a%d1/b%d1-1.)>.01) then
+    return
+  end if
+  if(abs(a%d2/b%d2-1.)>.01) return
+  if(abs(a%d3/b%d3-1.)>.01) return
+
+  res=.true.
+end function
+
+subroutine clean_modeling(modelingS)
+  type(modelingT) :: modelingS
+   deallocate(modelingS%b,modelingS%e)
+end subroutine
+
+
+end module

### 2016-08-20 src/acoustic-3d-fortran/prop_mod.f90

@@ -1,0 +1,246 @@
+module prop_mod
+  use modeling_mod
+  use resample_mod
+  use vel_mod
+  use sep
+  implicit none
+  real, private :: factor,gamma
+  real, private :: b_b(20)
+  type waveT
+    real,allocatable :: dat(:,:,:)
+  end type
+
+  interface
+
+ end interface
+
+  contains
+
+subroutine initWavefields(cur,p1,p2,p3)
+  type(modelingT) :: cur
+  type(waveT) :: p1,p2,p3
+    allocate(p1%dat(cur%n1,cur%n2,cur%n3))
+    allocate(p2%dat(cur%n1,cur%n2,cur%n3))
+    allocate(p3%dat(cur%n1,cur%n2,cur%n3))
+end subroutine
+
+subroutine cleanWavefields(p1,p2,p3)
+  type(waveT) :: p1,p2,p3
+  deallocate(p1%dat,p2%dat,p3%dat)
+end subroutine
+
+subroutine propWave(prev,cur,new,vsq,d1a,d2a,d3a,d0,b,e,b1,e1)
+  real  :: prev(:,:,:),cur(:,:,:),new(:,:,:),vsq(:,:,:)
+  double precision  :: d1a(:),d2a(:),d3a(:)
+  real   ::d0,gamma,factor
+  integer :: b(:),e(:),b1,e1
+  real ::d11,d12,d13,d14,d15,d21,d22,d23,d24,d25,d31,d32,d33,d34,d35
+  integer :: i1,i2,i3
+  real :: tau,taucur,tauprev, tmp
+
+  d11=d1a(1); d12=d1a(2); d13=d1a(3); d14=d1a(4); d15=d1a(5);
+  d21=d2a(1); d22=d2a(2); d23=d2a(3); d24=d2a(4); d25=d2a(5);
+  d31=d3a(1); d32=d3a(2); d33=d3a(3); d34=d3a(4); d35=d3a(5);
+
+    !write(0,*) "CHECK D11",d11,d21
+  ! call seperr("")
+  do i3=b(3),e(3)
+    do i2=b(2),e(2)
+      do i1=b(1),e(1)
+        new(i1,i2,i3)=vsq(i1,i2,i3)*(&
[…]

### 2016-08-20 src/acoustic-3d-fortran/resample_mod.f90

@@ -1,0 +1,256 @@
+module resample_mod
+  use modeling_mod
+  use sinc_mod
+  use sep
+  implicit none
+  real, allocatable :: sinc_table(:,:)
+  integer,private :: ns
+
+
+contains
+
+  subroutine init_sinc_table(nsinc,npts)
+    integer :: nsinc,npts
+    real    :: loc
+    integer :: n,i
+
+    allocate(sinc_table(nsinc,npts))
+    ns=nsinc
+    call mksinc_table(npts,nsinc,sinc_table)
+
+    i = sep_put_data_axis_par("sinc.H", 1, nsinc, 0., 0.,'nsinc')
+    i = sep_put_data_axis_par("sinc.H", 2, npts, 0., 0.,'npts')
+    i = srite("sinc.H", sinc_table, size(sinc_table)*4)
+
+  end subroutine
+
+  function floatsum2d(matrix) result(s)
+    real :: matrix(:,:)
+    real :: s
+    integer :: i1, i2
+
+    s = 0
+    do i2 = 1, size(matrix, 2)
+      do i1 = 1, size(matrix, 1)
+        s = s + matrix(i1, i2)
+      end do
+    end do
+
+  end function floatsum2d
+
+  subroutine write1di(file, dat, n1)
+    character(len=*) :: file
+    integer :: dat(:)
+    integer :: n1, ierr
+
+    ierr = sep_put_data_axis_par(file, 1, n1, 0.0, 0.0, '1')
+    ierr = sep_put_data_axis_par(file, 2, 1, 0.0, 0.0, '2')
+    ierr = srite(file, dat, size(dat) * 4)
+
+  end subroutine
+
+  subroutine write2di(file, dat, n1, n2)
+    character(len=*) :: file
+    integer :: dat(:,:)
+    integer :: n1, n2, ierr
+
+    ierr = sep_put_data_axis_par(file, 1, n1, 0.0, 0.0, '1')
+    ierr = sep_put_data_axis_par(file, 2, n2, 0.0, 0.0, '2')
+    ierr = srite(file, dat, size(dat)*4)
+
+  end subroutine
+
+  subroutine interpField(oldS,newS,oldF,newF,extend)
+    logical :: extend
+    type(modelingT) :: oldS,newS
+    real :: oldf(:,:,:), newf(:,:,:)
+    integer,allocatable:: t3(:),t2(:),t1(:)
[…]

### 2016-08-20 src/acoustic-3d-fortran/septimers.f90

@@ -1,0 +1,141 @@
+module sep_timer_type_mod
+
+type septimer
+logical :: active
+character(len=128) :: tag
+real*8 :: tot_time
+real*8 :: last_time
+integer :: ncalls
+end type
+end module
+
+module sep_timers_mod
+use sep_timer_type_mod
+type(septimer) :: timers(100)
+integer,private,save :: ilast
+
+
+
+contains
+
+logical function init_sep_timers()
+integer :: i
+init_sep_timers=.false.
+do i=1,100
+  call clear_time(timers(i))
+end do
+init_sep_timers=.true.
+ilast=0
+end  function
+
+subroutine print_timers()
+integer :: i
+
+do i=1,100
+ call print_timer(timers(i))
+end do
+
+end subroutine
+
+subroutine print_timer(st)
+type(septimer) :: st
+if(st%active) then
+write(0,*) trim(st%tag), "=tag ncalls=",st%ncalls," tot_time=",st%tot_time
+end if
+
+end subroutine
+
+subroutine stop_timer_num(inum)
+call stop_timer(timers(inum))
+end subroutine
+
+subroutine stop_timer(st)
+type(septimer) :: st
+st%tot_time=st%tot_time+get_time()-st%last_time
+st%ncalls=st%ncalls+1
+end subroutine
+
+subroutine start_timer_num(inum)
+call start_timer(timers(inum))
+end subroutine
+
+subroutine start_timer(st)
+type(septimer)::st
+st%last_time=get_time()
+end subroutine
+
+logical function setup_cycle_timer(tag,inum)
+character(len=*) :: tag
+integer :: inum
+setup_cycle_timer=setup_next_timer(tag,inum)
+end function
+logical function setup_next_timer(tag,inum)
+integer :: inum
+character(len=*) :: tag
+setup_next_timer=.false.
+if(ilast >99) then
+  write(0,*) "out of timers"
+  return
+end if
+ilast=ilast+1
+call setup_timer_num(ilast,tag)
+setup_next_timer=.true.
+inum=ilast
+end  function
+
+subroutine setup_timer_num(inum,tag)
+integer :: inum
+character(len=*) :: tag
+call setup_timer(timers(inum),tag)
+end subroutine
+
+
+subroutine setup_timer(st,tag)
+type(septimer) :: st
+character(len=*) :: tag
+st%tag=tag
+st%tot_time=0.
+st%active=.true.
+st%ncalls=0
+end subroutine
+
+subroutine clear_time(st)
[…]

### 2016-08-20 src/acoustic-3d-fortran/sinc_mod.f90

@@ -1,0 +1,34 @@
+module sinc_mod
+
+implicit none
+
+interface
+  subroutine mksincit(sinc,lsinc,d,space) bind(c,name="mksincit")
+    use iso_c_binding
+    implicit none
+    real(C_FLOAT),dimension(*),intent(out) :: sinc,space
+    integer(C_INT),value,intent(in) :: lsinc
+    real(C_FLOAT),value,intent(in) :: d
+  end subroutine
+end interface
+contains
+
+
+subroutine mksinc_table(nt,nsinc,table)
+  integer :: nt,nsinc,it;
+  real :: table(:,:),dtab,t,space(1000)
+
+  dtab=1.
+  dtab=1./nt
+  t=0
+  do it=1,nt
+    call mksincit(table(:,it),nsinc,t,space)
+    t=(it-1)*dtab
+  end do
+end subroutine
+
+
+
+
+
+end module

### 2016-08-20 src/acoustic-3d-fortran/source_mod.f90

@@ -1,0 +1,93 @@
+module source_mod
+  use sep_mod
+  use sep
+  use modeling_mod
+  implicit none
+  type sourceT
+    real :: x,z,y
+    real  :: dt
+    real,allocatable :: dat(:)
+  end type
+  type Wavefield
+    real,allocatable :: ar(:,:,:)
+  end type
+  type sourceW
+    type(Wavefield), dimension(:),allocatable :: W
+  end type
+contains
+
+  subroutine  initSourceSave(source,nb)
+    type(sourceW) :: source
+    integer :: nb
+    allocate(source%W(nb))
+  end subroutine
+
+  subroutine cleanSourceSave(source)
+    type(sourceW) :: source
+    integer :: i
+    do i=1,size(source%W)
+      deallocate(source%w(i)%ar)
+    end do
+    deallocate(source%w)
+  end subroutine
+
+  subroutine setSourceLocation(source,loc)
+    type(sourceT) :: source
+    real :: loc(:)
+
+    source%x=loc(1)
+    source%y = loc(2)
+  end subroutine
+
+
+  subroutine readSource(tag,src)
+    character(len=*) :: tag
+    type(sourceT) :: src
+    integer :: nt
+    real :: dt, ot
+    real, allocatable :: tmp(:)
+    character(len=128) :: tmpS
+    integer :: ierr
+
+
+    ierr= sep_get_data_axis_par(tag,1,nt,ot,dt,tmpS)
+
+    call from_param("src_z",src%z)
+    call from_param("src_y", src%y)
+
+    src%dt=dt
+
+    allocate(tmp(nt))
+    ierr=sreed(tag,tmp,size(tmp)*4)
+    allocate(src%dat(8+nt))
+    src%dat(1:4)=0
+    src%dat(5:4+nt)=tmp
+    src%dat(nt-3:)=0
+    deallocate(tmp)
+
+  end subroutine
+
+
+  subroutine addSource(src,tm,rnew,cur,scale)
+    type(sourceT) :: src
+    real :: tm
+    integer :: it,ix,iy,iz,ibase,isinc
+    real :: rnew(:,:,:)
+    real :: scale
+    type(modelingT) :: cur
+    real,pointer :: sincT(:)
+    it=tm/src%dt
+    isinc=(tm-it*src%dt)/src%dt*10000+1
[…]

### 2016-08-20 src/acoustic-3d-fortran/vel_mod.f90

@@ -1,0 +1,111 @@
+module vel_mod
+  use resample_mod
+  use modeling_mod
+  use sep_mod
+  use sep
+  implicit none
+  real,private :: w0,qfact,gamma,pi
+  type(modelingT) :: initialS
+  type velT
+    integer :: n1, n2, n3
+    real    :: o1, o2, o3
+    real    :: d1, d2, d3
+    real, allocatable, dimension(:,:,:) :: dat,vgamma
+  end type
+contains
+
+  subroutine readVel(fle,vel,full)
+    character(len=*)  :: fle
+    type(velT) :: vel
+    type(modelingT) :: full
+    character(len=128) :: junk
+    integer :: ierr,i1,i2,i3
+
+    ierr= sep_get_data_axis_par(fle,1,vel%n1,vel%o1,vel%d1,junk)
+    ierr= sep_get_data_axis_par(fle,2,vel%n2,vel%o2,vel%d2,junk)
+    ierr= sep_get_data_axis_par(fle,3,vel%n3,vel%o3,vel%d3,junk)
+
+
+    call from_param("qfact",qfact,50.)
+    call from_param("w0",w0,60.)
+    write(0, *), "vel (n1, n2, n3): (", vel%n1, vel%n2, vel%n3, ")"
+    write(0, *), "qfact: ", qfact
+    write(0, *), "w0: ", w0
+
+    pi=atan(1.)*4.
+    gamma=1./pi*atan(2*pi/qfact)
+    allocate(vel%dat(vel%n1,vel%n2, vel%n3))
+    ierr=sreed(fle,vel%dat,size(vel%dat)*4)
+
+    !do i3=1,vel%n3
+      !do i2=1,vel%n2
+        !do i1=1,vel%n1
+          !if (abs(vel%dat(i1,i2,i3) - 2000) > 0.0001) then
+            !write(0,*) 'vel /= 2000'
+            !call exit()
+          !end if
+        !end do
+      !end do
+    !end do
+    !vel%dat=1500
+
+    initialS%n1=vel%n1; initialS%o1=vel%o1; initialS%d1=vel%d1
+    initialS%n2=vel%n2; initialS%o2=vel%o2; initialS%d2=vel%d2
+    initialS%n3=vel%n3; initialS%o3=vel%o3; initialS%d3=vel%d3
[…]

### 2016-08-20 config/config.sh
rename folders

@@ -7,6 +7,7 @@ fi
 
 # madagascar
 export DATAPATH=${HOME}/.rsfdata/
+mkdir -p $DATAPATH
 export PYTHONPATH=$PYTHONPATH:$RSFSRC/build/book/Recipes
 
 # cuda

### 2016-08-20 src/acoustic-2d-fortran/main.fix.f90

@@ -1,0 +1,59 @@
+# 1 "<stdin>"
+# 1 "<built-in>"
+# 1 "<command-line>"
+# 1 "<stdin>"
+program RTM_FAST
+  use migrate_shot_mod
+  use sep
+  logical :: verb
+  type(velT) :: vel
+  type(timesT) :: times
+  type(sourceT) :: source
+  type(dataT) :: dat
+  type(modelingT) :: full
+  integer :: ishot,ii
+  real :: factor,rnd
+  integer, allocatable :: shot(:)
+  logical, allocatable :: shotL(:)
+
+
+  dfdf
+  call initpar()
+  call setup_timers()
+
+  !SETUP global migration parameters
+  call start_timer_num(timerInit)
+  call from_param("verbose",verb,.false.)
+  call readVel("vel",vel,full)
+  call initData("data",dat)
+  call calcImage(vel,"img")
+  call readSource("source",source)
+  call initTimes(times)
+  call initBox(dat,source,vel,verb)
+
+  call init_sinc_table(8,10000)
+  call stop_timer_num(timerInit)
+
+
+  allocate(shot(dat%n3),shotL(dat%n3))
+  shotL=.false.
+  ishot=1
+  do while(ishot<=dat%n3)
+    call random_number(rnd)
+    ii=max(1,min(dat%n3,nint(rnd*dat%n3)+1))
+    if(.not. shotL(ii)) then
+      shot(ishot)=ii
+      ishot=ishot+1
+    end if
+  end do
+
+
+  do ishot=1,dat%n3
+      factor= migrate_shot(shot(ishot),verb,vel,dat,source,times)
+      write(0,*) ishot," MIGRATING SHOT", shot(ishot), " of ",dat%n3, " sped up ",factor
+      if(mod(ishot,5)==0) call writeFullImage("img")
+  end do
+  call print_timers()
+  call writeFullImage("img")
+
+end program

### 2016-08-20 src/acoustic-3d-fortran/Make.py

@@ -1,0 +1,149 @@
+#!python 
+
+# Make Builder: Runs make.
+#
+# Parameters:
+#    MakePath -- SCons Dir node representing the directory in which to run make.  REQUIRED.
+#    MakeCmd -- The 'make' executable to run.
+#               Default: make
+#    MakeEnv -- Dictionary of variables to set in the make execution environment.
+#               Default: none
+#    MakeOpts -- Options to pass on the make command line.
+#                Default: none
+#    MakeOneThread -- Don't pass any -j option to make.
+#                     Default: False
+#    MakeTargets -- String of space-seperated targets to pass to make
+#                   Default: ""
+
+import os
+import subprocess
+
+from SCons.Script import *
+
+def parms(target, source, env):
+    """Assemble various Make parameters."""
+
+    if 'MakePath' in env.Dictionary().keys():
+        make_path = env.subst(str(env['MakePath']))
+    else:
+        print "Make builder requires MakePath variable"
+        Exit(1)
+
+    make_cmd = 'make'
+    if 'MakeCmd' in env.Dictionary().keys():
+        make_cmd = env.subst(env['MakeCmd'])
+    elif 'MAKE' in env.Dictionary().keys():
+        make_cmd = env.subst(env['MAKE'])
+
+    make_env = None
+    if env['CROSS_BUILD']:
+        make_env = env['CROSS_ENV']
+    if 'MakeEnv' in env.Dictionary().keys():
+        if make_env == None:
+            make_env = {}
+        else:
+            # We're appending to an existing dictionary, so create a copy
+            # instead of appending to the original env['CROSS_ENV']
+            make_env = env['CROSS_ENV'][:]
+        for (k,v) in env['MakeEnv'].items():
+            make_env[k] = v
+
+    make_opts = None
+    if 'MakeOpts' in env.Dictionary().keys():
+        make_opts = env.subst(env['MakeOpts'])
+
+    make_jobs = GetOption('num_jobs')
+    if 'MakeOneThread' in env.Dictionary().keys() and env['MakeOneThread']:
+        make_jobs = 1
+
+    make_targets = None
+    if 'MakeTargets' in env.Dictionary().keys():
+        make_targets = env.subst(env['MakeTargets'])
+
+    return (make_path, make_env, make_targets, make_cmd, make_jobs, make_opts)
+
+def message(target, source, env):
+    """Return a pretty Make message"""
+
+    (make_path,
+     make_env,
[…]

### 2016-08-20 src/acoustic-3d-fortran/main.fix.f90

@@ -1,3 +1,7 @@
+# 1 "<stdin>"
+# 1 "<built-in>"
+# 1 "<command-line>"
+# 1 "<stdin>"
 program RTM_FAST
   use my_timers_mod
   use vel_mod
@@ -11,12 +15,14 @@ program RTM_FAST
   type(velT) :: vel
   type(timesT) :: times
   type(sourceT) :: source
-  type(dataT)   :: dat
+  type(dataT) :: dat
   type(modelingT) :: full
   integer :: ishot,ii
   real :: factor,rnd
   integer, allocatable :: shot(:, :, :) ! first dimension store the real index
   logical, allocatable :: shotL(:, :)
+
+  sdfdf
 
   call initpar()
   call setup_timers()
@@ -60,7 +66,7 @@ program RTM_FAST
     do ixshot = 1, dat%n4
       factor= migrate_shot(shot(:, ixshot, iyshot),verb,vel,dat,source,times)
       write(0,*) ixshot, " MIGRATING SHOT", shot(1, ixshot, iyshot), " of ",dat%n4, " sped up ",factor
-      !if(mod(ishot,5)==0)  call writeFullImage("img")
+      !if(mod(ishot,5)==0) call writeFullImage("img")
     end do
   end do
   call print_timers()

### 2016-08-20 src/elastic-3d-cpu/fdutil.h

@@ -1,5 +1,3 @@
-/* This file is automatically generated. DO NOT EDIT! */
-
 #ifndef _fdutil_h
 #define _fdutil_h
 
@@ -188,11 +186,11 @@ fdm2d fdutil_init(bool verb_,
 
 
 /*------------------------------------------------------------*/
-fdm3d fdutil3d_init(bool verb_, 
+fdm3d fdutil3d_init(bool verb_,
 		    bool free_,
-		    sf_axis az_, 
-		    sf_axis ax_, 
-		    sf_axis ay_, 
+		    sf_axis az_,
+		    sf_axis ax_,
+		    sf_axis ay_,
 		    int     nb_,
 		    int ompchunk_);
 /*< init fdm utilities >*/
@@ -218,40 +216,40 @@ void offgridadj(float **ti,
 
 
 /*------------------------------------------------------------*/
-void expand(float** a, 
-	    float** b, 
+void expand(float** a,
+	    float** b,
 	    fdm2d fdm);
 /*< expand domain >*/
 
 
 /*------------------------------------------------------------*/
-void wpad2d(float **out, 
-	    float **inp, 
+void wpad2d(float **out,
+	    float **inp,
 	    fdm2d   fdm);
 /*< pad wavefield >*/
 
 
-void wpad3d(float ***out, 
-	    float ***inp, 
+void wpad3d(float ***out,
+	    float ***inp,
 	    fdm3d    fdm);
 /*< pad wavefield >*/
 
 
-void wwin2d(float **out, 
-	    float **inp, 
+void wwin2d(float **out,
+	    float **inp,
 	    fdm2d   fdm);
 /*< win wavefield >*/
 
 
-void wwin3d(float ***out, 
-	    float ***inp, 
+void wwin3d(float ***out,
+	    float ***inp,
 	    fdm3d    fdm);
 /*< win wavefield >*/
 
 
 /*------------------------------------------------------------*/
-void expand3d(float ***a, 
-	      float ***b, 
+void expand3d(float ***a,
+	      float ***b,
 	      fdm3d  fdm);
 /*< expand domain >*/
 
@@ -260,7 +258,7 @@ void expand3d(float ***a,
 void cut2d(float**  a,
 	   float**  b,
 	   fdm2d  fdm,
-	   sf_axis cz, 
+	   sf_axis cz,
 	   sf_axis cx);
 /*< cut a rectangular wavefield subset >*/
 
[…]

### 2016-08-20 src/elastic-3d-cpu/main-efd3d.c

@@ -1,21 +1,3 @@
-/* 3D elastic time-domain FD modeling */
-/*
-  Copyright (C) 2008 Colorado School of Mines
-
-  This program is free software; you can redistribute it and/or modify
-  it under the terms of the GNU General Public License as published by
-  the Free Software Foundation; either version 2 of the License, or
-  (at your option) any later version.
-
-  This program is distributed in the hope that it will be useful,
-  but WITHOUT ANY WARRANTY; without even the implied warranty of
-  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-  GNU General Public License for more details.
-
-  You should have received a copy of the GNU General Public License
-  along with this program; if not, write to the Free Software
-  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
-*/
 #include <rsf.h>
 #ifdef _OPENMP
 #include <omp.h>
@@ -25,44 +7,6 @@
 
 #include <sys/time.h>
 #define NOP 4 /* derivative operator half-size */
-
-/* Muir's derivative operator */
-/*#define C1 +0.598144 */
-/*  1225/ 1024      /2 */
-/*#define C2 -0.039876 */
-/* -1225/(1024*  15)/2 */
-/*#define C3 +0.004785 */
-/*  1225/(1024* 125)/2 */
-/*#define C4 -0.000348 */
-/* -1225/(1024*1715)/2 */
-
-/*  forward FD derivative stencils */
-/*#define Fx(a,ix,iy,iz,s) (C4*(a[iy  ][ix+4][iz  ] - a[iy  ][ix-3][iz  ]) + \*/
-/*              C3*(a[iy  ][ix+3][iz  ] - a[iy  ][ix-2][iz  ]) + \*/
-/*              C2*(a[iy  ][ix+2][iz  ] - a[iy  ][ix-1][iz  ]) + \*/
-/*                          C1*(a[iy  ][ix+1][iz  ] - a[iy  ][ix  ][iz  ]) )*s*/
-/*#define Fy(a,ix,iy,iz,s) (C4*(a[iy+4][ix  ][iz  ] - a[iy-3][ix  ][iz  ]) + \*/
-/*              C3*(a[iy+3][ix  ][iz  ] - a[iy-2][ix  ][iz  ]) + \*/
[…]

### 2016-08-20 src/q-elasgpu/Mfatomo.c

@@ -1,427 +1,0 @@
-/* First-arrival Traveltime Tomography */
-/*
-  Copyright (C) 2009 University of Texas at Austin
-  
-  This program is free software; you can redistribute it and/or modify
-  it under the terms of the GNU General Public License as published by
-  the Free Software Foundation; either version 2 of the License, or
-  (at your option) any later version.
-  
-  This program is distributed in the hope that it will be useful,
-  but WITHOUT ANY WARRANTY; without even the implied warranty of
-  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-  GNU General Public License for more details.
-  
-  You should have received a copy of the GNU General Public License
-  along with this program; if not, write to the Free Software
-  Foundation, Inc., 59 Temple Place, Suite 330, Boston, MA  02111-1307  USA
-*/
-
-#include <rsf.h>
-
-#include "fastmarch.h"
-#include "fatomo.h"
-
-#include "l1.h"
-#include "l1step.c"
-
-int main(int argc, char* argv[])
-{
-    bool adj, velocity, l1norm, plane[3], verb;
-    int dim, i, count, n[SF_MAX_DIM], it, nt, **m, nrhs, is, nshot=1, *flag, order, iter, niter, stiter, *k, nfreq, nmem;
-    float o[SF_MAX_DIM], d[SF_MAX_DIM], **t, *t0, *s, *temps, **source, *rhs, *ds;
-    float rhsnorm, rhsnorm0, rhsnorm1, rate, eps, gama;
-    char key[4], *what;
-    sf_file sinp, sout, shot, time, reco, rece, topo, grad, norm;
-    sf_weight weight=NULL;
-
-    sf_init(argc,argv);
-    sinp = sf_input("in");
-    sout = sf_output("out");
-
-    if (NULL == (what = sf_getstring("what"))) what="tomo";
-    /* what to compute (default tomography) */
-
-    switch (what[0]) {
-	case 'l': /* linear operator */
-
-	    if (NULL == sf_getstring("time"))
-		sf_error("Need time=");
[…]

### 2016-08-20 src/q-elasgpu/main-test.c

@@ -1,600 +1,0 @@
-#include <rsf.h>
-#include <assert.h>
-#include "fdutil.h"
-#include "common.h"
-#include "step-forward.h"
-#include "box.h"
-#include "check.h"
-#include "vel.h"
-#include "resample.h"
-
-fdm3d mkfdm(bool verb, bool fsrf, const modeling_t *m)
-{
-  int nbd = m->nb;
-  sf_axis az = sf_maxa(m->n1 - 2 * m->nb, m->o1 + nbd * m->d1, m->d1);
-  sf_axis ax = sf_maxa(m->n2 - 2 * m->nb, m->o2 + nbd * m->d2, m->d2);
-  sf_axis ay = sf_maxa(m->n3 - 2 * m->nb, m->o3 + nbd * m->d3, m->d3);
-
-  return fdutil3d_init(verb,fsrf,az,ax,ay,nbd,1);
-}
-
-int main(int argc, char** argv)
-{
-
-  bool verb, fsrf, snap, expl, dabc, cden, adj;
-  bool optfd, hybrid, sinc;
-  int jsnap, jdata;
-
-  /* I/O files */
-  sf_file file_wav=NULL; /* wavelet */
-  sf_file file_vel=NULL; /* velocity */
-  sf_file file_den=NULL; /* density */
-  sf_file file_wfl=NULL; /* wavefield */
-  sf_file file_dat=NULL; /* data */
-  sf_file file_src=NULL; /* sources */
-  sf_file file_rec=NULL; /* receivers */
-
-  /* cube axes */
-  sf_axis at = NULL, az = NULL, ax = NULL, ay = NULL;
-  sf_axis as = NULL, ar = NULL;
-
-  int nbd;  /* ABC boundary size */
-  int fdorder;  /* finite difference spatial accuracy order */
-  int nzpad,nxpad,nypad; /* boundary padded model size */
-  int ix,iy,it,nx,ny,nz,nt,ns,nr;
-  float ox,oy,oz,dx,dy,dz,dt,dt2;
-  float* damp=NULL; /* damping profile for hybrid bc */
-  float* ws;  /* wavelet */
-  float*** vel=NULL;  /* velocity */
-  float*** rho=NULL; /* density */
-  float*** u0=NULL;  /* wavefield array u@t-1 (u@t+1) */
-  float*** u1=NULL;  /* wavefield array u@t */
[…]

### 2016-08-20 config/config.sh
update config.sh

@@ -1,4 +1,6 @@
 #!/bin/bash
+# vim: fdm=marker fdl=0
+# vim: ft=sh
 
 # Intel version 14
 if [[ -d /usr/local/intel_14 ]]; then
@@ -15,6 +17,8 @@ export LD_LIBRARY_PATH=/usr/local/cuda/lib64:$LD_LIBRARY_PATH
 
 # SEPLIB
 export SEP=/data/bob/SEP
+
+# setup SEPLIB#{{{
 newPATH87=${SEP:?'required environment variable SEP missing'}/bin:${PATH}
 if [ ! -d ${SEP} ] ; then
   echo "${SEP} is not a directory. Exiting ..."
@@ -38,3 +42,4 @@ else
   export LANG
 fi
 unset newPATH87
+#}}}

### 2016-08-20 scripts/bnr.sh
remove uncessary files

@@ -1,7 +1,0 @@
-#!/bin/bash
-
-jobdir=$PWD
-rootdir=../../
-cd $rootdir; scons -j4 && \
-  cd $jobdir; rm -rf ./VTId-3d-GPU.rsf; scons
-

### 2016-08-20 src/acoustic-2d-fortran/main.fix.f90

@@ -1,59 +1,0 @@
-# 1 "<stdin>"
-# 1 "<built-in>"
-# 1 "<command-line>"
-# 1 "<stdin>"
-program RTM_FAST
-  use migrate_shot_mod
-  use sep
-  logical :: verb
-  type(velT) :: vel
-  type(timesT) :: times
-  type(sourceT) :: source
-  type(dataT) :: dat
-  type(modelingT) :: full
-  integer :: ishot,ii
-  real :: factor,rnd
-  integer, allocatable :: shot(:)
-  logical, allocatable :: shotL(:)
-
-
-  dfdf
-  call initpar()
-  call setup_timers()
-
-  !SETUP global migration parameters
-  call start_timer_num(timerInit)
-  call from_param("verbose",verb,.false.)
-  call readVel("vel",vel,full)
-  call initData("data",dat)
-  call calcImage(vel,"img")
-  call readSource("source",source)
-  call initTimes(times)
-  call initBox(dat,source,vel,verb)
-
-  call init_sinc_table(8,10000)
-  call stop_timer_num(timerInit)
-
-
-  allocate(shot(dat%n3),shotL(dat%n3))
-  shotL=.false.
-  ishot=1
-  do while(ishot<=dat%n3)
-    call random_number(rnd)
-    ii=max(1,min(dat%n3,nint(rnd*dat%n3)+1))
-    if(.not. shotL(ii)) then
-      shot(ishot)=ii
-      ishot=ishot+1
-    end if
-  end do
-
-
-  do ishot=1,dat%n3
-      factor= migrate_shot(shot(ishot),verb,vel,dat,source,times)
-      write(0,*) ishot," MIGRATING SHOT", shot(ishot), " of ",dat%n3, " sped up ",factor
-      if(mod(ishot,5)==0) call writeFullImage("img")
-  end do
-  call print_timers()
-  call writeFullImage("img")
-
-end program

### 2016-09-19 paper/paris17/paper.tex
add paris17

--- 2016-08-20 src/acoustic-2d-fortran/paper.tex
@@
-\title{Approximating Q propagation to speed up finite differences}
-\author{Robert G. Clapp}
-\righthead{Approximate Q}
-\lefthead{Clapp}
-\footer{SEP--158}
-\maketitle
-
-\begin{abstract}
-
-%Motivation
-
-Propagating wave-fields using explicit finite difference is the kernel for Reverse Time Migration (RTM) and high end velocity analysis
-algorithms.
-To avoid grid dispersion artifacts,  the cost of propagation is proportional to the frequency of the energy being propagated raised
-to the fourth power.
-Attenuation in the earth tends to decrease usable frequencies as a function of time.
-By using an approximation to the wave equation for attenuated media, to save computation, we can approximate the earth's behavior.
-As a result we can use coarser sampling at large time. Combined
-with limiting  grid propagation to around the source at early times we can achieve large speedups in modeling, migration, and potentially
-velocity analysis.
-\end{abstract}
-
-%Approach
-%Results
-%Conslussions
+\documentclass{paris17}
+\begin{document}
 
 \section{Introduction}
-Imaging and velocity analysis are the most computationally intensive parts
-of seismic processing. As a results researchers are always trying
-to find ways to speedup these processes \cite[]{bednar,Stork}.
-One approach used to speed up downward continuation based
-algorithms is to recognize that the earth attenuates seismic signals.
-As a result, as we push the wave-field down in depth, we can ignore
-higher and higher frequencies and still obtain an accurate image\cite[]{Clapp.sep.111.bob3}.
-This approach lowers the cost as you increase in depth. This technique is well
-suited for downward continuation based approaches which are done
-frequency by frequency.
-Reducing the frequencies downward
-continued as a function of depth  is particularly effective in combination with recognizing
-that there was no reason to propagate waves a large distance from
-the source at early times. 
-While following the wavefield is used routinely in RTM,  taking
-advantage of attenuation is not commonly used.  Reasons include:
-the cost of propagation with an attenuated wave equation, 
-attenuation is a function of medium parameter, and propagation 
-is generally done in the the time, rather frequency domain.
-\par
-In this paper I use a constant-Q approximation based on the work of \cite{zhu}.  As
-I propagate my source I resample my medium based on the maximum frequency that has not
-been significantly attenuated. Combining this approach with following the wave-field,
-I show that I can achieve significant computational speedups.
 
-\section{Modeling}
+Imaging and velocity analysis are the most computationally intensive parts of seismic processing.
+As a results researchers are always trying to find ways to speedup these processes \cite[]{bednar,Stork}.
+One approach used to speed up downward continuation based algorithms is to recognize that the earth attenuates seismic signals.
+As a result, as we push the wave-field down in depth, we can ignore higher and higher frequencies and still obtain an accurate image\cite[]{Clapp.sep.111.bob3}.
+This approach lowers the cost as you increase in depth.
+This technique is well suited for downward continuation based approaches which are done frequency by frequency.
+Reducing the frequencies downward continued as a function of depth  is particularly effective in combination with recognizing that there was no reason to propagate waves a large distance from the source at early times.
+While following the wavefield is used routinely in RTM,  taking advantage of attenuation is not commonly used.
+Reasons include: the cost of propagation with an attenuated wave equation, attenuation is a function of medium parameter, and propagation is generally done in the the time, rather frequency domain.
+
+In this paper I use a constant-Q approximation based on the work of \cite[]{zhu}.
+As I propagate my source I resample my medium based on the maximum frequency that has not been significantly attenuated.
+Combining this approach with following the wave-field, I show that I can achieve significant computational speedups.
+
+\section{Method and Theory}
+
+\subsection{Modeling}
 
@@
 For stability the Courant-Friedrichs-Lewy condition \cite[]{courant1967partial} must be met.
-Stability is a function of limiting what percentage of a grid cell energy can move in one time step. Stability is therefore a function of the maximum velocity 
-$v_{max}$, the minimum spatial sampling 
-$d_{min}$, and the time step $dt$. For stability,
+Stability is a function of limiting what percentage of a grid cell energy can move in one time step.
+Stability is therefore a function of the maximum velocity $v_{max}$, the minimum spatial sampling $d_{min}$, and the time step $dt$.
+For stability,
+
 \begin{equation}
@@
 \end{equation}
+
 The stability condition pushes one to use larger spatial sampling (faster, but less resolution) and/or finer time sampling (more expensive).
@@
 of points. For the purpose of this paper I will require  3.2  points therefore,
+
 \begin{equation}
@@
 \end{equation}
-The dispersion constraint pushes us towards smaller (more expensive) spatial sampling, because of the stability constraint, and results in smaller the
-steps.
+
+The dispersion constraint pushes us towards smaller (more expensive) spatial sampling, because of the stability constraint, and results in smaller the steps.
 Minimizing dispersion is the real reason for the expense of finite differences.
 To avoid grid dispersion and achieve the same level of stability the number of operations increase by the fourth power (three due to space sampling and one for time).
-\par
+
 From observation we know that the earth attenuates acoustic signals.
 Attenuation varies as a function of frequency and earth materials.
-The first approximation I am going to use is the concept of the constant
-Q model introduced by \cite{Kjartansson.sep.23}. 
+The first approximation I am going to use is the concept of the constant Q model introduced by \cite{Kjartansson.sep.23}.
 Q is defined as
+
 \begin{equation}
@@
 \end{equation}
-where $\frac{E}{\partial E}$ is the fraction of energy lost per cycle. The larger the $Q$ value, the less energy loss per cycles.
- The constant Q assumption assumes that energy dies out is a function of the number of wavelengths traveled through a medium. The higher the frequency, the faster the energy is attenuated.
-\subsection{Constant-Q Formulation}
-Building on this foundation \cite{zhu} used a fractional Laplacian approach to perform attenuated  propagation 
-in the time domain. Given a forcing function $f(t)$ and the wave-field $P(t)$ they proposed the equation,
-\begin{equation}
-\left[ \eta \bf L + \tau \bf H \frac{d}{dt} - v^{-2} \frac{\partial^2}{\partial t^2}\right] P(t)=f(t) \label{eq:zhu1},
-\end{equation}
-where 
-\begin{eqnarray}
-\bf L = \left(-\nabla^2\right)^{\gamma+1} \\
-\bf H = \left(-\nabla^2\right)^{\gamma+\frac{1}{2}}.
-\end{eqnarray}
-The constants in equation \ref{eq:zhu1} are defined as 
-\begin{equation}
-\eta=-v^{2\gamma}w_0^{-2\gamma} \cos \pi \gamma,
-\end{equation}
 
-\begin{equation}
-\tau=-v^{2\gamma-1}w_0^{-2\gamma} \sin \pi \gamma,
-\end{equation}
-and 
-\begin{equation}
-\gamma=\frac{1}{\tan^{-1}\frac{1}{Q}}.
-\end{equation}
-The first term in equation \ref{eq:zhu1} deals the dispersive effect of attenuation. The middle term
-deals damping.  For a constant Q approximation I can further simplify equation~\ref{eq:zhu1}, approximating
-$\nabla^2$ for $\bf H$. My resulting equation is then
-\begin{equation}
-\left[ \nabla^2 - \tau \nabla^2 \frac{d}{dt} - v^{-2} \frac{\partial^2}{\partial t^2}\right] P(t) =f(t) \label{eq:use}.
-\end{equation}
-\par
-Figure \ref{fig:qnoq} shows the wave-field using the standard acoustic wave equation (left) and an attenuation wave-field (right). Note
-the difference in the frequency content. This is can be more clearly seen in
-Figure \ref{fig:spectra} which shows the spectrum of wave-field at $.3,1.3,2.3$, and $3.3$ seconds with $Q=200$. Notice the energy
-decay of frequency over time. 
-The key observation is that there is no reason to worry about dispersion at frequencies that have attenuated.
-Specifically, I  redo my dispersion calculation (equation \ref{eq:dispersion}) several times while propagating
-a wave-field.
-At each time block I use a $f_{max}$ based on frequencies whose energy has not been reduced more than some percentage (in this paper 96\%).
-As a result,  as I forward propagate in time my grid cells, and if I desire,  time sampling,
-get larger.  
-Figure~\ref{fig:timeQ} shows the speedup factor (defined as the number of grid cells times time steps) as a function of propagation time for different Q values.
-The longer the time record, the more using Q pays off in terms speed up.
-Using this approach the early time steps dominate the computation.  For example assuming an initial maximum frequency of 
-$90Hz$ and a constant velocity of $2000 m/s$, a Q value of $200$, the total speedup is $4$ even though  most of the 
-propagation time  shows significantly more speedup. Figure~\ref{fig:qtot} shows the speedups for Q values ranging from 150 to 350.
+where $\frac{E}{\partial E}$ is the fraction of energy lost per cycle.
+The larger the $Q$ value, the less energy loss per cycles.
+The constant Q assumption assumes that energy dies out is a function of the number of wavelengths traveled through a medium.
+The higher the frequency, the faster the energy is attenuated.
 
-\plot{qnoq}{width=6.0in}{The wave-field with the standard acoustic wave equation (left) and the attenuated wave-field (right) at the same time.\ER}
+\subsection{Constant Q formulation}
 
-\sideplot{spectra}{width=3.0in}{The frequency of the wave-field at various times.  Note the reduction of the high frequencies over time. Note at .3 seconds,
-total amplitude is less because the source has not been fully injected into the medium.\ER}
+\section{Examples (Optional)}
 
-\sideplot{timeQ}{width=2.5in}{Speedup values as a function of propagation time for Q values ranging from 150 to 350.  Note how the longer the time record the more the computation is sped up.\ER}
-\sideplot{qtot}{width=2.5in}{Total speedup for different values of Q.
-Note the relatively small speedups compared to what one might expect looking at Figure~\ref{fig:timeQ}.
-Total time is the inverse of the sum of the inverses of speedups.\ER}
-\par
-Another speedup trick used by many when doing modeling/migration is to recognize that there is no need to propagate the wave-fields significantly away from the source
-at early times.  The number of cells we need to propagate increases as a  power of three (expanding wave-field)
-in modeling, and somewhat less in migration due to the spatial extent of our receivers.
-This speedup trick is most effective at early times and useless at late times when energy has propagated throughout the model, the  opposite
-behavior as the constant-Q trick. Figure~\ref{fig:follow}  shows a typical wide azimuth geometry and
-the speedup as a function of time again assuming $2 km/s$ medium. Total speedup for
-following the source is only 2-2.5.   
-Combining the two tricks is where we begin to see big payoffs.
-The left plot of Figure~\ref{fig:timeTot} shows the result of combining the two approaches for different values of
-Q.  The right plot shows the total speedup as a function of Q.  Note how the maximum cost is in the $1$ to $3$ second range
-depending on the value of Q.  Without following the wave-field the total speedup ranged from  1.8 to 4, we now get speedups between 15 and 250.
-\sideplot{follow}{width=2.5in}{Speedup by following the wave-field in the case of modeling a single shot and in the case of an array of receivers. Note how
-these curves move in the opposite direction to those in Figure~\ref{fig:timeQ}.\ER}
-\plot{timeTot}{width=6.0in}{The left plot shows speed up as a function of propagation time for a series of Q values. The right plot shows the total
-speedup as a function of Q. Note on the left how total speedup is a combination of the trends shown in Figures~\ref{fig:timeQ} and \ref{fig:follow}. Note
-on the right the significant speedup compared to those shown in Figure~\ref{fig:qtot}.\ER} Calculating speedup numbers is far from an exact science.
-My choice of a low constant velocity helps me by improving the speedups due to following the wave-field and hurts me by allowing larger time steps.
-Computational
-time and the number of grid cells do not completely linear relation. Smaller grids, means better cache behavior, and can lead
-to significant improvements in performance. In addition my propagator is more
-expensive than the standard acoustic propagator which isn't taken into account.
+This is the first sentence of the example section.
 
-\begin{algorithm} \caption{Forward propagation} \label{alg:forward}
-\begin{algorithmic}[1]
-\FOR{timeblock 0...n}
-\STATE{Calculate max frequency of interest relevant at the beginning of time window}
-\STATE{Calculate max extent of wave-field at end of time window}
-\STATE{Calculate sampling of medium and time based on stability/dispersion constraints}
-\STATE{Resample wave-field and velocity}
-\FOR {t=0...n in timeblock}
-\STATE{ Propagate wave-field with Q approximation}
-\STATE{Inject source}
-\IF{Imaging step}
-\STATE{Store wave-field}
-\ENDIF
-\ENDFOR
-\ENDFOR
- \end{algorithmic}
-\end{algorithm}
+\section{Results (Optional)}
 
-The basic algorithm for modeling is shown in Algorithm~\ref{alg:forward}.  Figure~\ref{fig:sampleCompare} shows the wave-field propagating through
-a relatively complex synthetic after 2 seconds using resampling tricks (left) and a static grid (right).  
-\plot{sampleCompare}{width=6.0in}{The left panel shows the wave-field using a static grid, the 
-right panel using the approach outline in algorithm~\ref{alg:forward} both using equation~\ref{eq:use}. Note the low frequency artifact in the right panel, but otherwise
-the plots are nearly identical.\ER}
+This is the first sentence of the result section.
 
-\section{Migration}
-Applying the method described above to RTM is relatively straightforward. Modeling is done using the
-approach outlined in algorithm~\ref{alg:forward}.  Back propagation starts with low frequencies
-and then increases in frequency at smaller times.  For real data there is no need to 
-use the approximate Q propagator because the whole assumption of this approach is that
-there is no useful information at high frequencies at large times. The back projection 
-step is described in algorithm~\ref{alg:backward}.
-
-\begin{algorithm} \caption{Backward propagation for real data}\label{alg:backward}
-\begin{algorithmic}[1]
-\FOR{timeblock n...0}
-\STATE{Calculate max frequency of interest relevant at the beginning of time window}
-\STATE{Calculate max extent of wave-field at end of time window}
-\STATE{Calculate sampling of medium and time based on stability/dispersion constraints}
-\STATE{Resample wave-field, velocity}
-\STATE{Resample temp image to full image and sum}
-\STATE{Create temp image}
-\FOR {t=n..0 in timeblock}
-\STATE{ Propagate wave-field}
-\STATE{Inject source}
-\IF{Imaging step}
-\STATE{Apply imaging condition store in temp image}
-\ENDIF
-\ENDFOR
-\ENDFOR
- \end{algorithmic}
-\end{algorithm}
-Figure~\ref{fig:single} shows the result of migrating a single shot using a standard static grid, left, and a changing grid, right.  There is significantly
-more noise, particularly away from the main energy train, using the variable grid, but the main energy train is nearly identical. Figure~\ref{fig:full}
-shows the result of migrating an entire dataset using the changing grid method. After summing all the shots the artifacts seen in Figure~\ref{fig:single}
-have disappeared.
-\plot{single}{width=6.0in}{The left plot shows the result of migrating a single shot using a static grid, the right plot shows the result using
-the changing grid described by algorithms \ref{alg:forward} and \ref{alg:backward}.  Note the spurious energy away from the main energy
-train using the changing grid.\ER}
-\plot{full}{width=6.0in}{The result of migrating an entire dataset using the changing grid approach. Note how the artifacts seen in Figure~\ref{fig:single}
-are not apparent in the final migration.\CR}
-\section{Discussion}
-The tests shown in this paper are limited to modeling and migration. Another obvious area to apply
-these techniques is velocity analysis. For waveform inversion techniques that rely on low frequencies this approach
-will lead to minimal speedup advantages but the cheap approximation of attenuation might prove useful.
-The big advantage is for  Wave Equation Migration Velocity Analysis\cite[]{Zhang.sep.152.yang1} and Total Full Waveform Inversion\cite[]{Almomin.sep.155.ali1} techniques.
-In addition to potentially a better approximation of matching the physics of the real data, these technique
-are interested in large time records and higher frequencies, which is where this approach leads to significant performance
-improvments.  The reduction in data size,  resulting
-from coarser sampling of the wave-field could also prove useful.
+% \begin{figure}[!htb]
+%   \centering
+%   \includegraphics[width=0.6\textwidth]{....eps}
+%   \caption{...}
+% \end{figure}
 
 \section{Conclusions}
-I use an approximation to \cite{zhu} to simulate propagation in an attenuated earth. I take
-advantage of the fact that frequencies decay with time by resampling my propagation grid
-at later times. Combining this approach with following the wave-field leads to
-significant speedups in modeling and RTM. The approach is also
-potentially useful for Wave Equation Migration Velocity Analysis and Total
-Full Waveform Inversion.
 
-\section{Acknowledgements}
-I would like to thank Yi Shen for the time-domain approximate-Q formulation and Gustavo Alves for
-the initial discussion that brought on this idea. I would like than Total for providing the
-data used in this paper.
+This is the first sentence of the conclusions.
 
-\bibliographystyle{seg}
-\bibliography{SEP,bob}
+\section{Acknowledgements (Optional)}
+
+This is the first sentence of the acknowledgements.
+
+\bibliography{bob}
+
+\end{document}

### 2016-09-20 paper/paris17/paper.tex
add formular

@@
 \documentclass{paris17}
+\usepackage{amsmath}
 \begin{document}
@@
 
+Our theory is built on the foundation of \cite[]{zhu2014theory}.
+It is a time-domain differential equation for modelling seismic wave propagation in constant-Q viscoelastic media based on fractional spatial derivatives, specifically Laplacian differential operators of fractional order.
+The stress–strain relation is derived from the classical equation expressed in terms of fractional time derivatives.
+The formulation has the advantage of not requiring additional field variables that increase the computer time and storage significantly \cite[]{zhu2014theory}.
+
+We first extend the formulation of \cite[]{zhu2014theory} from the 2D viscoelastic case to the 3D viscoelastic case.
+Note that the Laplacian differential operators of fractional order bring extra computational costs to the elastic modeling, we approximate it with the conventional Laplacian operators, which significantly reduces the computing complexities.
+Also, we further reduce the computational costs by ignoring the dispersion terms because it make little effects compared to the attenuation of the signals.
+As a result, our equation is then
+
+\begin{equation}
+\begin{bmatrix} \sigma_{11}\\ \sigma_{22}\\ \sigma_{33} \end{bmatrix} = \begin{bmatrix} \frac{\partial \tau_p^{(1)}}{\partial t} + c_{11} & \frac{\partial \tau_p^{(1)}}{\partial t} - 2\frac{\partial \tau_s^{(1)}}{\partial t} +c_{12}& \frac{\partial \tau_p^{(1)}}{\partial t} - 2\frac{\partial \tau_s^{(1)}}{\partial t} +c_{13} \\ \frac{\partial \tau_p^{(2)}}{\partial t} - 2\frac{\partial \tau_s^{(2)}}{\partial t} +c_{12}& \frac{\partial \tau_p^{(2)}}{\partial t} + c_{22} & \frac{\partial \tau_p^{(2)}}{\partial t} - 2\frac{\partial \tau_s^{(2)}}{\partial t} +c_{23}\\ \frac{\partial \tau_p^{(3)}}{\partial t} - 2\frac{\partial \tau_s^{(3)}}{\partial t} +c_{13} & \frac{\partial \tau_p^{(3)}}{\partial t} - 2\frac{\partial \tau_s^{(3)}}{\partial t} +c_{23} & \frac{\partial \tau_p^{(3)}}{\partial t} + c_{33} \end{bmatrix} \begin{bmatrix} \epsilon_{11}\\ \epsilon_{22}\\ \epsilon_{33} \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+  \sigma_{12} = \left ( 2\frac{\partial \frac{c_{11}-c_{12}}{2}c_s^{(2\gamma-1)}\sin(\pi\gamma_s)}{\partial t} + c_{66} \right )\times \epsilon_{12}
+\end{equation}
+%\begin{equation}
+%\begin{bmatrix}
+%\sigma_{11}\\
+%\sigma_{22}\\
+%\sigma_{33}
+%\end{bmatrix} =
+%\begin{bmatrix}
+%\frac{\partial \tau_p^{(1)}}{\partial t} + c_{11} & \frac{\partial \tau_p^{(1)}}{\partial t} - 2\frac{\partial \tau_s^{(1)}}{\partial t} +c_{12}& \frac{\partial \tau_p^{(1)}}{\partial t} - 2\frac{\partial \tau_s^{(1)}}{\partial t} +c_{13} \\
+  %\frac{\partial \tau_p^{(2)}}{\partial t} - 2\frac{\partial \tau_s^{(2)}}{\partial t} +c_{12}& \frac{\partial \tau_p^{(2)}}{\partial t} + c_{22} & \frac{\partial \tau_p^{(2)}}{\partial t} - 2\frac{\partial \tau_s^{(2)}}{\partial t} +c_{23}\\
+  %\frac{\partial \tau_p^{(3)}}{\partial t} - 2\frac{\partial \tau_s^{(3)}}{\partial t} +c_{13} &  \frac{\partial \tau_p^{(3)}}{\partial t} - 2\frac{\partial \tau_s^{(3)}}{\partial t} +c_{23}  & \frac{\partial \tau_p^{(3)}}{\partial t} + c_{33}
+%\end{bmatrix} \begin{bmatrix}
+%\epsilon_{11}\\
+%\epsilon_{22}\\
+%\epsilon_{33}
+%\end{bmatrix}
+  %\label{eq:q_approximation}
+%\end{equation}
+
+The spatial derivatives are calculated with a generalization of the Fourier pseudospectral method to the fractional-derivative case.
+The accuracy of the numerical solution is verified against an analytical solution in a homogeneous medium.
+An example shows that the proposed wave equation describes the constant-Q attenuation and velocity dispersion behaviour observed in Pierre Shale.
+Finally, we consider a plane-layer model and the Marmousi model to show how the new formulation applies to inhomogeneous media.
+
 \section{Examples (Optional)}

### 2016-09-20 paper/paris17/paper.tex
add text

--- 2016-09-19 paper/paris17/paper.tex
@@
 
+Our theory is built on the foundation of \cite[]{zhu2014theory}.
+It is a time-domain differential equation for modeling seismic wave propagation in constant-Q viscoelastic media based on fractional spatial derivatives, specifically Laplacian differential operators of fractional order.
+The stress–strain relation is derived from the classical equation expressed in terms of fractional time derivatives.
+The formulation has the advantage of not requiring additional field variables that increase the computer time and storage significantly \cite[]{zhu2014theory}.
+
+We first extend the formulation of \cite[]{zhu2014theory} from the 2D viscoelastic case to the 3D viscoelastic case.
+Note that the Laplacian differential operators of fractional order bring extra computational costs to the elastic modeling, we approximate it with the conventional Laplacian operators, which significantly reduces the computing complexities.
+Also, we further reduce the computational costs by ignoring the dispersion terms because it make little effects compared to the attenuation of the signals.
+As a result, our equations are then
+
+\begin{equation}
+\begin{bmatrix} \sigma_{11}\\ \sigma_{22}\\ \sigma_{33} \end{bmatrix} = \begin{bmatrix} \frac{\partial \tau_p^{(1)}}{\partial t} + c_{11} & \frac{\partial \tau_p^{(1)}}{\partial t} - 2\frac{\partial \tau_s^{(1)}}{\partial t} +c_{12}& \frac{\partial \tau_p^{(1)}}{\partial t} - 2\frac{\partial \tau_s^{(1)}}{\partial t} +c_{13} \\ \frac{\partial \tau_p^{(2)}}{\partial t} - 2\frac{\partial \tau_s^{(2)}}{\partial t} +c_{12}& \frac{\partial \tau_p^{(2)}}{\partial t} + c_{22} & \frac{\partial \tau_p^{(2)}}{\partial t} - 2\frac{\partial \tau_s^{(2)}}{\partial t} +c_{23}\\ \frac{\partial \tau_p^{(3)}}{\partial t} - 2\frac{\partial \tau_s^{(3)}}{\partial t} +c_{13} & \frac{\partial \tau_p^{(3)}}{\partial t} - 2\frac{\partial \tau_s^{(3)}}{\partial t} +c_{23} & \frac{\partial \tau_p^{(3)}}{\partial t} + c_{33} \end{bmatrix} \begin{bmatrix} \epsilon_{11}\\ \epsilon_{22}\\ \epsilon_{33} \end{bmatrix}
+\end{equation}
+
+\begin{equation}
+  \sigma_{12} = \left ( 2\frac{\partial}{\partial t} \left( \frac{c_{11}-c_{12}}{2}c_s^{(2\gamma_s-1)}\sin(\pi\gamma_s) \right) + c_{66} \right )\times \epsilon_{12}
+\end{equation}
+
+\begin{equation}
+  \sigma_{13} = \left ( 2\frac{\partial}{\partial t} \left( \frac{c_{33}-c_{13}}{2}c_s^{(2\gamma_s-1)}\sin(\pi\gamma_s) \right) + c_{55} \right )\times \epsilon_{13}
+\end{equation}
+
+\begin{equation}
+  \sigma_{23} = \left ( 2\frac{\partial}{\partial t} \left( \frac{c_{22}-c_{23}}{2}c_s^{(2\gamma_s-1)}\sin(\pi\gamma_s) \right) + c_{44} \right )\times \epsilon_{23}
+\end{equation}
+
+\begin{equation}
+  \tau_p^{(1)} = c_{11}C_p^{2\gamma_p - 1}\sin(\pi \gamma_p)
+\end{equation}
+
+\begin{equation}
+  \tau_s^{(1)} = \frac{c_{11} - c_{13}}{2}C_s^{2\gamma_s - 1}\sin(\pi \gamma_s)
+\end{equation}
+
+\begin{equation}
+  \gamma_{p,s}=\frac{1}{\pi}\tan^{-1}(\frac{1}{Q_{p,s}})
+\end{equation}
+
+where $\sigma$ is the stress tensor; $\epsilon$ is the strain tensor; $c_{ij}$ is the forth-order stiffness tensor; $C_p$ and $C_s$ are the velocities of P-wave and S-wave.
+$Q_{p,s}$ is the constant factor for the attenuation of P-wave and S-wave respectively.
+Note that we only present how $\tau_p^{(1)}$ and $\tau_s^{(1)}$ are derived, $\tau_p^{(2)}$,$\tau_p^{(3)}$, $\tau_s^{(2)}$ and $\tau_s^{(3)}$ can be derived in a similar way.
+
+Our constant Q formulation is relatively computationally economic because we preserve the original workflow of elastic modeling while adding a few terms in the calculation of stress tensors from train tensors.
+
+\subsection{GPU optimizations}
+
 \section{Examples (Optional)}

### 2016-09-20 paper/paris17/paper.tex
add experiments

@@
 
+\section{Experiments}
+
+Figure xxx shows the wave-field using the standard acoustic wave equation (left) and an attenuation wave-field (right).
+Note the difference in the frequency content.
+This is can be more clearly seen in Figure xxx which shows the spectrum of wave-field at 0.9 seconds with $Q_p = Q_s = 20$.
+Notice the energy decay of frequency over time.
+The key observation is that there is no reason to worry about dispersion at frequencies that have attenuated.
+Specifically, I redo my dispersion calculation (equation 2) several times while propagating a wave-field.
+At each time block I use a fmax based on frequencies whose energy has not been reduced more than some percentage (in this paper 96\%).
+As a result, as I forward propagate in time my grid cells, and if I desire, time sampling, get larger.
+Figure 3 shows the speedup factor (defined as the number of grid cells times time steps) as a function of propagation time for different Q values.
+The longer the time record, the more using Q pays off in terms speed up.
+Using this approach the early time steps dominate the computation.
+For example assuming an initial maximum frequency of 90Hz and a constant velocity of 2000m/s, a Q value of 200, the total speedup is 4 even though most of the propagation time shows significantly more speedup.
+Figure 4 shows the speedups for Q values ranging from 150 to 350.
+
+Another speedup trick used by many when doing modeling/migration is to recognize that there is no need to propagate the wave-fields significantly away from the source at early times.
+The number of cells we need to propagate increases as a power of three (expanding wave-field) in modeling, and somewhat less in migration due to the spatial extent of our receivers.
+This speedup trick is most effective at early times and useless at late times when energy has propagated throughout the model, the opposite behavior as the constant-Q trick.
+Combining the two tricks is where we begin to see big payoffs.
+The left plot of Figure 6 shows the result of combining the two approaches for different values of Q.
+
+Table xxx shows the performance speedup on using different number of GPUs.
+Through combining the GPU optimization schemes above, the GPU design amoung four K40 cards improve the performance by upto xxx times over xxx cores.
+Note that the CPU design is also tuned by using multi-threading and vectorizations.
+
+The memory optimizations achieve the best usage of the hierarchical GPU spaces, while tuning the register usage per thread reaches a tradeoff to maximize the computing efficiency.
+Furthermore, the halo updating is largely hidden within the computations.
+So we achieve an inspiring performance speedup.
+
 \section{Examples (Optional)}

### 2016-10-20 paper/paris17/paper.tex
add text to GPU optimizations

@@
 
+The reason why GPUs outperforms CPUs significantly on many scenarios is that the architecture of GPUs favors throughput of many data-parallel tasks over the latency of a single thread.
+We have an efficient parallel design on the GPU platform with three main strategies.
+
+Firstly, we fully utilize the different hierarchical memory of the GPU.
+We keep a set of constant variables such as the derivative coefficients in the constant memory and the read-only cache.
+As the 64KB first-level cache can be configured as different combinations between L1 cache and shared memory, we configure it dynamically based on different computing scenarios.
+For the stencil computation, we configure the first-level cache by setting the sizes of shared memory and L1 cache to be 48 KB and 16 KB, respectively, which achieves a high computation performance based on P.
+Micikevicius’ 3D stencil design.
+For others, we prefer to configure the first-level cache as L1 cache if we don't use memory explicitly.
+
 \section{Experiments}

### 2016-12-29 paper/paris17/paper.tex
add figures

@@
 \usepackage{amsmath}
+\usepackage{graphicx}
+\usepackage{graphicx}
+\usepackage{caption}
+\usepackage{subcaption}
+\usepackage{floatrow}
+% Table float box with bottom caption, box width adjusted to content
+\newfloatcommand{capbtabbox}{table}[][\FBwidth]
+\usepackage{capt-of}% or \usepackage{caption}
+\usepackage{booktabs}
+\usepackage{varwidth}
+
 \begin{document}
@@
 Stability is therefore a function of the maximum velocity $v_{max}$, the minimum spatial sampling $d_{min}$, and the time step $dt$.
-For stability,
-
-\begin{equation}
-v_{max}\frac{dt}{d_{min}} < .5 \label{eq:stability}.
-\end{equation}
+For stability, we have $v_{max}\frac{dt}{d_{min}} < .5$.
 
@@
 There isn't a consensus on the minimum number
-of points. For the purpose of this paper I will require  3.2  points therefore,
-
-\begin{equation}
-\frac{v_{min} }{f_{max}d_{max}} > 3.2 \label{eq:dispersion}.
-\end{equation}
+of points. For the purpose of this paper I will require  3.2  points therefore, we have $\frac{v_{min} }{f_{max}d_{max}} > 3.2 \label{eq:dispersion}$.
 
@@
 The first approximation I am going to use is the concept of the constant Q model introduced by \cite{Kjartansson.sep.23}.
-Q is defined as
-
-\begin{equation}
-Q=2 \pi \left( \frac{E}{\partial E}\right),
-\end{equation}
-
-where $\frac{E}{\partial E}$ is the fraction of energy lost per cycle.
+Q is defined as $Q=2 \pi \left( \frac{E}{\partial E}\right)$, where $\frac{E}{\partial E}$ is the fraction of energy lost per cycle.
 The larger the $Q$ value, the less energy loss per cycles.
@@
 Micikevicius’ 3D stencil design.
-For others, we prefer to configure the first-level cache as L1 cache if we don't use memory explicitly.
+For others, we prefer to configure the first-level cache as L1 cache if we don't use shared memory explicitly.
+
+Secondly, we carefully tune the number of registers per thread to maximize the occupancy of GPUs.
+Since the access pattern of GPU global memory in the stencil kernel is irregular, the more threads are busy, the less latencies it is for memory access.
+However, as the number of registers is limited in a streaming multiprocessor (SM), increasing the number of registers per threads will decrease the number of active warps.
+So it is important to have a strategy to balance them.
+We first remove the intermediate variables to reduce the number of registers per threads.
+Then we dynamically tracking the performance by adjusting the block size and the \emph{maxrregcount} compiler option.
+
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[height=1.3in]{./fig/domain-decompose.pdf}
+        \caption{Domain decomposition}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[height=1.3in]{./fig/inner-outer.pdf}
+        \caption{Task decomposition}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[height=1.1in]{./fig/overlap.pdf}
+        \caption{Comp. \& Comm. overlapping}
+    \end{subfigure}
+    \caption{Computation and communication overlapping over multiple GPUs.}
+\end{figure}
 
@@
 
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[height=1.3in]{./fig/std.pdf}
+        \caption{Wavefield without attenuation}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[height=1.3in]{./fig/q20.pdf}
+        \caption{Wavefield with attenuation}
+    \end{subfigure}
+    ~ 
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[height=1.3in]{./fig/spec.eps}
+        \caption{Spectrum of the wavefields}
+    \end{subfigure}
+    \caption{Wavefields with and without attenuation.}
+\end{figure}
+
 Another speedup trick used by many when doing modeling/migration is to recognize that there is no need to propagate the wave-fields significantly away from the source at early times.
@@
 Note that the CPU design is also tuned by using multi-threading and vectorizations.
+\begin{figure}[h]
+    \centering
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[height=1.5in]{./fig/speedup.eps}
+%        \caption{Wavefield without attenuation}
+    \end{subfigure}%
+    ~ 
+    \begin{subfigure}[b]{0.4\textwidth}
+        \centering
+        \includegraphics[height=1.5in]{./fig/speedup_q.eps}
+%        \caption{Wavefield with attenuation}
+    \end{subfigure}
+    \caption{Wavefields with and without attenuation.}
+\end{figure}
 
@@
 
-\section{Examples (Optional)}
-
-This is the first sentence of the example section.
-
-\section{Results (Optional)}
-
-This is the first sentence of the result section.
-
-% \begin{figure}[!htb]
-%   \centering
-%   \includegraphics[width=0.6\textwidth]{....eps}
-%   \caption{...}
-% \end{figure}
-
 \section{Conclusions}
@@
 
-\section{Acknowledgements (Optional)}
-
-This is the first sentence of the acknowledgements.
-
 \bibliography{bob}

### 2016-12-29 paper/paris17/fig/performance.m

@@ -1,0 +1,21 @@
+cpu = [1   1   1 ];
+gpu1 = [27   1.5   19 ];
+gpu2 = [50   1.8   36];
+gpu4 = [94   2   62];
+
+sum(cpu)
+sum(gpu1)
+sum(gpu2)
+data = [cpu; gpu1; gpu2; gpu4];
+
+bar(data);
+
+legend({'Commp.',  'Extract & save',  'Total'}, 'Location','Best');
+title('Speedup of GPUs over CPUs', 'fontsize', 14);
+set(gca, 'xticklabel', {'24-core CPUs', '1 GPU', '2 GPUs', '4 GPUs'},'fontsize',12)
+%axis([0,10,0,100])
+ylabel('Speedup')
+grid minor
+set(gca, 'FontSize', 14);
+%end
+

### 2016-12-29 paper/paris17/fig/spec.m

@@ -1,0 +1,12 @@
+q20 = importdata('q20-9.txt');
+std = importdata('std-9.txt');
+X = [1 : size(q20)];
+figure(1);
+
+plot(X, q20, X, std);
+
+legend('Q_s = Q_p = 20', 'Standard', 'Location', 'Best');
+xlabel('Wave number');
+ylabel('Amplitude');
+grid minor
+set(gca,'FontSize',14)

### 2016-12-29 paper/paris17/fig/speedup_q.m

@@ -1,0 +1,16 @@
+q100 = [204 100 90 120 130 150 180 190];
+q150 = [190 90 85 110 120 140 160 170];
+q200 = [150 85 77 107 110 115 130 135];
+q250 = [130 80 70 90 100 106 114 120];
+X = [1:8];
+
+figure(1);
+
+plot(X, q100, '-o', X, q150, '-+', X, q200, '-*', X, q250, '-d','LineWidth',2);
+xlabel('Time (s)');
+ylabel('Speedup');
+title('Speedup of different Q value');
+legend('q=100', 'q=150', 'q=200', 'q=250', 'Location', 'Best');
+grid minor
+set(gca, 'FontSize', 14);
+

### 2016-12-29 src/acoustic-3d-fortran/main.f90

@@ -1,1 +1,69 @@
-main_old.f90
+program RTM_FAST
+  use my_timers_mod
+  use vel_mod
+  use data_mod
+  use image_mod
+  use source_mod
+  use box_mod
+  use migrate_shot_mod
+  use sep
+  logical :: verb
+  type(velT) :: vel
+  type(timesT) :: times
+  type(sourceT) :: source
+  type(dataT)   :: dat
+  type(modelingT) :: full
+  integer :: ishot,ii
+  real :: factor,rnd
+  integer, allocatable :: shot(:, :, :) ! first dimension store the real index
+  logical, allocatable :: shotL(:, :)
+
+  call initpar()
+  call setup_timers()
+
+  !SETUP global migration parameters
+  call start_timer_num(timerInit)
+  call from_param("verbose",verb,.false.)
+  call readVel("vel",vel,full)
+  call initData("data",dat)
+  call calcImage(vel,"img")
+  call readSource("source",source)
+  call initTimes(times)
+  call initBox(dat,source,vel,verb)
+
+  call init_sinc_table(8,10000)
+  call stop_timer_num(timerInit)
+
+
+  allocate(shot(2, dat%n4, dat%n5), shotL(dat%n4, dat%n5))
+  shotL=.false.
+
+  write(0,*) 'dat%n4',dat%n4, ' dat%n5', dat%n5
+
+  ! ASK: what's doing in 2D cases?
+  iyshot=1
+  do while(iyshot<= dat%n5)
+    ixshot = 1
+    do while(ixshot<= dat%n4)
+      call random_number(rnd)
+      ii=max(1,min(dat%n4,nint(rnd*dat%n4)+1))
+      jj=max(1,min(dat%n5,nint(rnd*dat%n5)+1))
+      if(.not. shotL(ii, jj)) then
+        shot(:,ixshot, iyshot)=(/ii, jj/)
+        ixshot = ixshot + 1
+      end if
+    end do
+    iyshot = iyshot + 1
+  end do
+
+  do iyshot = 1, dat%n5
+    do ixshot = 1, dat%n4
+      factor= migrate_shot(shot(:, ixshot, iyshot),verb,vel,dat,source,times)
+      write(0,*) ixshot, " MIGRATING SHOT", shot(1, ixshot, iyshot), " of ",dat%n4, " sped up ",factor
+      !if(mod(ishot,5)==0)  call writeFullImage("img")
+    end do
+  end do
+  call print_timers()
+  call writeFullImage("img")
+
+end program

### 2016-12-29 paper/paris17/paper.tex
add SConstruct

@@
 For stability, we have $v_{max}\frac{dt}{d_{min}} < .5$.
-
 The stability condition pushes one to use larger spatial sampling (faster, but less resolution) and/or finer time sampling (more expensive).
@@
 
+Thirdly, we design a computation and communication overlapping scheme to maximize the concurrency of different resources.
+The entire wavefield domain is divided into 4 subdomain, each assigning to a GPU shown in Figure \ref{fig:domain-decomposition}.
+Note that we need ghost cells to store and exchanges the halos, denoted by the arrows.
+In each subdomain, we further divide it into three parts, the halo part, the outer part and the inner part shown in Figure \ref{fig:task-decomposition}.
+The computation of inner and outer parts are assigned to different CUDA streams so that they are executed concurrently.
+When the computation of the outer part is finished, the GPU starts exchanging halos with its neighbors.
+In this way, the computation of the inner part can hide the communication shown in Figure \ref{fig:overlap}.
+
 \begin{figure}[h]
@@
         \caption{Domain decomposition}
+        \label{fig:domain-decomposition}
     \end{subfigure}%
@@
         \caption{Task decomposition}
+        \label{fig:task-decomposition}
     \end{subfigure}
@@
         \caption{Comp. \& Comm. overlapping}
+        \label{fig:overlap}
     \end{subfigure}
@@
 This is can be more clearly seen in Figure xxx which shows the spectrum of wave-field at 0.9 seconds with $Q_p = Q_s = 20$.
+
 Notice the energy decay of frequency over time.

### 2016-12-31 paper/paris17/paper.tex
draft

@@
 
-Imaging and velocity analysis are the most computationally intensive parts of seismic processing.
-As a results researchers are always trying to find ways to speedup these processes \cite[]{bednar,Stork}.
-One approach used to speed up downward continuation based algorithms is to recognize that the earth attenuates seismic signals.
-As a result, as we push the wave-field down in depth, we can ignore higher and higher frequencies and still obtain an accurate image\cite[]{Clapp.sep.111.bob3}.
-This approach lowers the cost as you increase in depth.
-This technique is well suited for downward continuation based approaches which are done frequency by frequency.
-Reducing the frequencies downward continued as a function of depth  is particularly effective in combination with recognizing that there was no reason to propagate waves a large distance from the source at early times.
-While following the wavefield is used routinely in RTM,  taking advantage of attenuation is not commonly used.
-Reasons include: the cost of propagation with an attenuated wave equation, attenuation is a function of medium parameter, and propagation is generally done in the the time, rather frequency domain.
+Propagating wavefields using explicit finite difference method is the kernel of reverse time migration (RTM) and high-end velocity algorithms in seismic applications.
+In recent decades there has been a significant increase of interest in the seismic exploration community to reconstruct the image of the underground in larger regions and higher resolutions, especially in the elastic media.
+As a result the optimizing methods to improving the performance of the wavefield propagation are in great demands.
 
-In this paper I use a constant-Q approximation based on the work of \cite[]{zhu}.
-As I propagate my source I resample my medium based on the maximum frequency that has not been significantly attenuated.
-Combining this approach with following the wave-field, I show that I can achieve significant computational speedups.
+%As the Earth attenuates the seismic signals in real Earth materials, an accuracy wavefield modeling approach needs to account for the effects of attenuation and velocity dispersion \cite[]{zhu2014theory}.
+
+One approach to improve the performance of modeling is to recognize that the earth attenuates seismic energies, in which case, we can ignore higher and higher frequencies and still obtain an accurate image\cite[]{Clapp.sep.111.bob3} when we push the wavefield down in depth.
+By using coarser sampling at large time steps,  the performance for downward continuation based approaches which are done frequency by frequency can be significantly improved.
+
+The concept of the constant Q model introduced by \cite{Kjartansson.sep.23} are used to approximate the attenuation.
+However, the formulation for computing the time derivative for the constant Q model proposed by Podlubny requires to store wavefields from previous values to present time \cite[]{podlubny1998fractional}, which is impractical for real seismic modeling in terms on memory capacities on modern computers.
+Zhu developed a constant-Q wave equation using fractional Laplacian operators to avoid the need of storing the past values of the wavefields \cite[]{zhu2014theory}.
+However, the proposed method is for 2D viscoelastic case and the computation of fractional Laplacian is expensive compared with the conventional FD methods.
+
+Meanwhile, the Nvidia Graphic Processing Units (GPUS)  have achieved great successes in many domains.
+In seismic application, GPUs are employed as high-performance computing accelerators for key seismic modeling, imaging and inversion kernels due to their high memory bandwidth and a large number of processing units \cite[]{ohmer2005implementation,he2015gpu}.
+
+This work proposes a high performance design of accelerating the wavefield propagation in 3D elastic media by approximating the constant Q propagation on multiple Nvidia GPUs.
+We first propose the Q approximation formulation by extending the formulation from the 2D viscoelastic to the 3D viscoelastic case where the fractional Laplacian is approximated to the conventional Laplacian and the dispersion term is ignored.
+Optimization strategies from different aspects (memory, occupancy, and overlapping) are performed to form a high performance modeling kernel on multiple GPUs.
+To further improve the performance, a couple of tricks are also applied to reduce the total computation.
+Combining all the optimization schemes, we can achieve a significant speedup of the 3D elastic wave propagation by 60 to 200 times over a highly optimized 24-core CPU solution.
 
@@
 
-\subsection{Modeling}
+%\subsection{Modeling}
 
-Explicit finite difference modeling is constrained by figuring  out a sampling in time and space that results in stable propagation and does not create dispersive events.
+%Explicit finite difference modeling is constrained by figuring  out a sampling in time and space that results in stable propagation and does not create dispersive events.
 For stability the Courant-Friedrichs-Lewy condition \cite[]{courant1967partial} must be met.
-Stability is a function of limiting what percentage of a grid cell energy can move in one time step.
+For stability, we have $v_{max}\frac{dt}{d_{min}} < .5$, where  $v_{max}$ is the maximum velocity; $dt$ is the
+
+%Stability is a function of limiting what percentage of a grid cell energy can move in one time step.
 Stability is therefore a function of the maximum velocity $v_{max}$, the minimum spatial sampling $d_{min}$, and the time step $dt$.
-For stability, we have $v_{max}\frac{dt}{d_{min}} < .5$.
-The stability condition pushes one to use larger spatial sampling (faster, but less resolution) and/or finer time sampling (more expensive).
+
+%The stability condition pushes one to use larger spatial sampling (faster, but less resolution) and/or finer time sampling (more expensive).
 Dispersion, on the other hand, is a function of the minimum velocity $v_{min}$, the maximum frequency $f_{max}$, and the maximum spaital sampling $d_{max}$.
@@
 There isn't a consensus on the minimum number
-of points. For the purpose of this paper I will require  3.2  points therefore, we have $\frac{v_{min} }{f_{max}d_{max}} > 3.2 \label{eq:dispersion}$.
+%of points. For the purpose of this paper I will require  3.2  points therefore, we have $\frac{v_{min} }{f_{max}d_{max}} > 3.2 \label{eq:dispersion}$.
 
-The dispersion constraint pushes us towards smaller (more expensive) spatial sampling, because of the stability constraint, and results in smaller the steps.
+%The dispersion constraint pushes us towards smaller (more expensive) spatial sampling, because of the stability constraint, and results in smaller the steps.
 Minimizing dispersion is the real reason for the expense of finite differences.
@@
 
-From observation we know that the earth attenuates acoustic signals.
-Attenuation varies as a function of frequency and earth materials.
+%Attenuation varies as a function of frequency and earth materials.
 The first approximation I am going to use is the concept of the constant Q model introduced by \cite{Kjartansson.sep.23}.
@@
 
-Our constant Q formulation is relatively computationally economic because we preserve the original workflow of elastic modeling while adding a few terms in the calculation of stress tensors from train tensors.
+The reason why our constant Q formulation is relatively computationally economic are: (1) The fractional Laplacian is approximated to the conventional Laplacian.
+(2) The dispersion term is ignored.
+(3) We preserve the original workflow of elastic modeling while only adding a few terms in the calculation of stress tensors from train tensors.
 
-\subsection{GPU optimizations}
+\subsection{GPU Optimizations}
 
@@
 
+\subsection{Other Optimization Tricks}
+
+Apart from the GPU-based optimization, we also apply another two approaches to further improve the performance.
+After we taking the energy attenuation into consideration, we can ignore the frequencies that have attenuated.
+As a result, the grid cells and the time steps get larger as the wavefield propagate in time.
+We can achieve significant speedup when we resample the velocities and wavefields to coarser grids, especially recording the longer time step.
+Using the above approach, the early time steps dominate the computation.
+We eliminate the bottleneck by applying another trick that we recognize that it is not necessary to propagate the wavefields significantly away from the source at early times.
+We eliminate the update of the wavefields where the waves have not reached so far.
+
 \section{Experiments}
 
-Figure xxx shows the wave-field using the standard acoustic wave equation (left) and an attenuation wave-field (right).
-Note the difference in the frequency content.
-This is can be more clearly seen in Figure xxx which shows the spectrum of wave-field at 0.9 seconds with $Q_p = Q_s = 20$.
-
-Notice the energy decay of frequency over time.
-The key observation is that there is no reason to worry about dispersion at frequencies that have attenuated.
-Specifically, I redo my dispersion calculation (equation 2) several times while propagating a wave-field.
-At each time block I use a fmax based on frequencies whose energy has not been reduced more than some percentage (in this paper 96\%).
-As a result, as I forward propagate in time my grid cells, and if I desire, time sampling, get larger.
-Figure 3 shows the speedup factor (defined as the number of grid cells times time steps) as a function of propagation time for different Q values.
-The longer the time record, the more using Q pays off in terms speed up.
-Using this approach the early time steps dominate the computation.
-For example assuming an initial maximum frequency of 90Hz and a constant velocity of 2000m/s, a Q value of 200, the total speedup is 4 even though most of the propagation time shows significantly more speedup.
-Figure 4 shows the speedups for Q values ranging from 150 to 350.
+\subsection{Q Effects}
+Experiments for demonstrating the functionality of applying the Q effects as well as  the performance with different optimization tricks are carried out in this paper.
+Figure \ref{fig:with-attenuation} shows a slice of the z-component of the 3D wavefield using standard elastic wave equation at time 0.9 seconds while the Figure \ref{fig:without-attenuation} shows the wavefields with the constant Q effect ($Q_s=Q_p=20$) added.
+The wave front in Figure \ref{fig:with-attenuation} is weaker.
+The spectrum of the wavefields gives a better illustration, which is shown in Figure \ref{fig:spectrum}.
 
@@
         \centering
-        \includegraphics[height=1.3in]{./fig/std.pdf}
-        \caption{Wavefield without attenuation}
-    \end{subfigure}%
+        \includegraphics[height=1.3in]{./fig/q20.pdf}
+        \caption{Wavefield with attenuation}
+        \label{fig:with-attenuation}
+    \end{subfigure}
     ~
@@
         \centering
-        \includegraphics[height=1.3in]{./fig/q20.pdf}
-        \caption{Wavefield with attenuation}
-    \end{subfigure}
+        \includegraphics[height=1.3in]{./fig/std.pdf}
+        \caption{Wavefield without attenuation}
+        \label{fig:without-attenuation}
+    \end{subfigure}%
     ~
@@
         \caption{Spectrum of the wavefields}
+        \label{fig:spectrum}
     \end{subfigure}
@@
 
-Another speedup trick used by many when doing modeling/migration is to recognize that there is no need to propagate the wave-fields significantly away from the source at early times.
-The number of cells we need to propagate increases as a power of three (expanding wave-field) in modeling, and somewhat less in migration due to the spatial extent of our receivers.
-This speedup trick is most effective at early times and useless at late times when energy has propagated throughout the model, the opposite behavior as the constant-Q trick.
-Combining the two tricks is where we begin to see big payoffs.
-The left plot of Figure 6 shows the result of combining the two approaches for different values of Q.
+\subsection{Performance}
 
-Table xxx shows the performance speedup on using different number of GPUs.
-Through combining the GPU optimization schemes above, the GPU design amoung four K40 cards improve the performance by upto xxx times over xxx cores.
-Note that the CPU design is also tuned by using multi-threading and vectorizations.
+We propagate the wavefield in the 3D domain of size $700\times700\times700$ for 6000 time steps to measure the performance.
+Figure \ref{fig:gpu-speedup} shows the performance speedup of 1-4 K40 GPUs over one 24-core CPU node.
+The GPU design among 4 K40 accelerator cards can improve the performance of the computational part by up to 96 times, and improve the overall performance by up to 63 times.
+Note that the CPU design is also tuned by using multi-threading and vectorization.
+Figure \ref{fig:q-speedup} shows the speedup factor, which is  defined as the number of grid cells times time steps, as a function of propagation time for different Q values.
+We can see that the longer the time records, we more significant performance speedup we achieve.
+Combing the two tricks as well as the GPU-based optimizations, we can achieve a performance speedup over 60 to 200 times as a function of Q.
+
 \begin{figure}[h]
@@
         \includegraphics[height=1.5in]{./fig/speedup.eps}
-%        \caption{Wavefield without attenuation}
+        \caption{Speedup with GPU optimizations}
+        \label{fig:gpu-speedup}
     \end{subfigure}%
@@
         \includegraphics[height=1.5in]{./fig/speedup_q.eps}
-%        \caption{Wavefield with attenuation}
+        \caption{Speedup of different Q value}
+        \label{fig:q-speedup}
     \end{subfigure}
-    \caption{Wavefields with and without attenuation.}
+    \caption{Performance speedup}
 \end{figure}
-
-The memory optimizations achieve the best usage of the hierarchical GPU spaces, while tuning the register usage per thread reaches a tradeoff to maximize the computing efficiency.
-Furthermore, the halo updating is largely hidden within the computations.
-So we achieve an inspiring performance speedup.
 
@@
 
-This is the first sentence of the conclusions.
+This work manages to boost the performance the wave propagation in 3D elastic scenarios by approximating the Q propagation and using GPU platforms.
+We first extends the constant-Q formulation from the 2D viscoelastic to 3D viscoelastic case.
+Different optimization techniques on GPUs are then described for a high performance modeling kernel.
+We also propose a set of tricks to reduce the computation to further reduce computations.
+The experimental results show that we can achieve significant performance speedup by 60 to 200 times over the CPU-based solution.
 

### 2017-01-01 paper/paris17/paper.tex
personal review

@@
 
-Propagating wavefields using explicit finite difference method is the kernel of reverse time migration (RTM) and high-end velocity algorithms in seismic applications.
-In recent decades there has been a significant increase of interest in the seismic exploration community to reconstruct the image of the underground in larger regions and higher resolutions, especially in the elastic media.
-As a result the optimizing methods to improving the performance of the wavefield propagation are in great demands.
+Propagating wavefields using the explicit finite difference method is the kernel of reverse time migration (RTM) and high-end velocity algorithms in seismic applications.
+In recent decades there has been a significant increase of interest in the seismic exploration community to invert the image of the subsurface in larger regions and higher resolutions in the elastic media, which brings tremendous computing challenges.
+As a result the optimizing methods for improving the performance of the wavefield propagation are in great demands.
 
@@
 
-One approach to improve the performance of modeling is to recognize that the earth attenuates seismic energies, in which case, we can ignore higher and higher frequencies and still obtain an accurate image\cite[]{Clapp.sep.111.bob3} when we push the wavefield down in depth.
-By using coarser sampling at large time steps,  the performance for downward continuation based approaches which are done frequency by frequency can be significantly improved.
+One approach to improve the performance of modeling is to recognize that the Earth attenuates seismic energy.
+We can ignore higher and higher frequencies and still obtain an accurate image\cite[]{Clapp.sep.111.bob3} when we push the wavefield down in depth.
+By using coarser sampling at large time steps based on the stability and dispersion conditions, we can reduce the computational cost for wavefield propagation.
 
 The concept of the constant Q model introduced by \cite{Kjartansson.sep.23} are used to approximate the attenuation.
-However, the formulation for computing the time derivative for the constant Q model proposed by Podlubny requires to store wavefields from previous values to present time \cite[]{podlubny1998fractional}, which is impractical for real seismic modeling in terms on memory capacities on modern computers.
-Zhu developed a constant-Q wave equation using fractional Laplacian operators to avoid the need of storing the past values of the wavefields \cite[]{zhu2014theory}.
-However, the proposed method is for 2D viscoelastic case and the computation of fractional Laplacian is expensive compared with the conventional FD methods.
+However, the formulation for computing the time derivative for the constant Q model requires to store wavefields from previous values to present time \cite[]{podlubny1998fractional}, which is impractical for real seismic modeling in terms of memory capacities on modern computers.
+Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoids the need of storing the past values of the wavefields \cite[]{zhu2014theory}.
+However, the proposed method is for 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.
 
-Meanwhile, the Nvidia Graphic Processing Units (GPUS)  have achieved great successes in many domains.
-In seismic application, GPUs are employed as high-performance computing accelerators for key seismic modeling, imaging and inversion kernels due to their high memory bandwidth and a large number of processing units \cite[]{ohmer2005implementation,he2015gpu}.
+Meanwhile, the Nvidia Graphic Processing Units (GPUS)  have achieved a great success in many domains.
+In seismic applications, GPUs are employed as high-performance computing accelerators for key seismic modeling, imaging and inversion kernels due to their high memory bandwidth and a large number of processing units \cite[]{he2015gpu}.
 
@@
 We first propose the Q approximation formulation by extending the formulation from the 2D viscoelastic to the 3D viscoelastic case where the fractional Laplacian is approximated to the conventional Laplacian and the dispersion term is ignored.
-Optimization strategies from different aspects (memory, occupancy, and overlapping) are performed to form a high performance modeling kernel on multiple GPUs.
-To further improve the performance, a couple of tricks are also applied to reduce the total computation.
-Combining all the optimization schemes, we can achieve a significant speedup of the 3D elastic wave propagation by 60 to 200 times over a highly optimized 24-core CPU solution.
+Optimization strategies from different aspects (memory, occupancy, and overlapping) are performed to form an efficient kernel on multiple GPUs.
+To further improve the performance, a set of tricks are also applied to reduce the computation.
+Combining all the optimization schemes, we can achieve a significant speedup of 60 to 200 times over a highly optimized 24-core CPU solution for the 3D elastic wavefield propagation.
 
@@
 
-Our theory is built on the foundation of \cite[]{zhu2014theory}.
-It is a time-domain differential equation for modeling seismic wave propagation in constant-Q viscoelastic media based on fractional spatial derivatives, specifically Laplacian differential operators of fractional order.
-The stress–strain relation is derived from the classical equation expressed in terms of fractional time derivatives.
-The formulation has the advantage of not requiring additional field variables that increase the computer time and storage significantly \cite[]{zhu2014theory}.
+Our theory is built on the foundation of \cite{zhu2014theory}.
+The time-domain differential equation is based on the Laplacian differential operators of fractional order, which is able to model seismic wave propagation in constant-Q viscoelastic media.
+The stress-strain relation is derived from the classical equation expressed in terms of fractional time derivatives.
+The formulation has the advantage of not requiring additional field variables so that it saves the computing time and storage significantly \cite[]{zhu2014theory}.
 
-We first extend the formulation of \cite[]{zhu2014theory} from the 2D viscoelastic case to the 3D viscoelastic case.
+We extend the formulation of \cite{zhu2014theory} from the 2D viscoelastic case to the 3D viscoelastic case.
 Note that the Laplacian differential operators of fractional order bring extra computational costs to the elastic modeling, we approximate it with the conventional Laplacian operators, which significantly reduces the computing complexities.
 Also, we further reduce the computational costs by ignoring the dispersion terms because it make little effects compared to the attenuation of the signals.
-As a result, our equations are then
+As a result, our equations are as follows.
 
@@
 
-The reason why our constant Q formulation is relatively computationally economic are: (1) The fractional Laplacian is approximated to the conventional Laplacian.
+The reasons why our constant Q formulation is relatively computationally economic are as follows.
+(1) The fractional Laplacian is approximated to the conventional Laplacian.
 (2) The dispersion term is ignored.
-(3) We preserve the original workflow of elastic modeling while only adding a few terms in the calculation of stress tensors from train tensors.
+(3) We preserve the original workflow of elastic modeling while only adding a few terms when computing stress tensors from train tensors.
 
@@
 
-The reason why GPUs outperforms CPUs significantly on many scenarios is that the architecture of GPUs favors throughput of many data-parallel tasks over the latency of a single thread.
-We have an efficient parallel design on the GPU platform with three main strategies.
+The reason why GPUs outperforms CPUs significantly on many scenarios is that the architecture of GPUs favors the throughput of many data-parallel tasks over the latency of a single thread.
+We have an efficient parallel design on the multiple-GPU platform with three main strategies.
 
-Firstly, we fully utilize the different hierarchical memory of the GPU.
+Firstly, we fully utilize the hierarchical memory of the GPU.
 We keep a set of constant variables such as the derivative coefficients in the constant memory and the read-only cache.
-As the 64KB first-level cache can be configured as different combinations between L1 cache and shared memory, we configure it dynamically based on different computing scenarios.
-For the stencil computation, we configure the first-level cache by setting the sizes of shared memory and L1 cache to be 48 KB and 16 KB, respectively, which achieves a high computation performance based on P.
-Micikevicius’ 3D stencil design.
-For others, we prefer to configure the first-level cache as L1 cache if we don't use shared memory explicitly.
+As the 64KB first-level cache can be configured as different combinations between L1 cache and shared memory, we configure it dynamically in different scenarios.
+For the 8th-order stencil computation, we configure the first-level cache by setting the sizes of shared memory and L1 cache to be 48 KB and 16 KB respectively, which achieves great performance based on the 3D stencil design proposed by \cite{micikevicius20093d}.
+For others, we prefer to configure the first-level cache as L1 cache where we don't use shared memory explicitly.
 
 Secondly, we carefully tune the number of registers per thread to maximize the occupancy of GPUs.
-Since the access pattern of GPU global memory in the stencil kernel is irregular, the more threads are busy, the less latencies it is for memory access.
-However, as the number of registers is limited in a streaming multiprocessor (SM), increasing the number of registers per threads will decrease the number of active warps.
+Since the access pattern of GPU global memory in the stencil kernel is irregular, the more threads there are, the less latency it gains for memory access.
+However, as the number of registers is limited in a streaming multiprocessor (SM), increasing the number of registers per thread will decrease the number of active warps.
 So it is important to have a strategy to balance them.
-We first remove the intermediate variables to reduce the number of registers per threads.
-Then we dynamically tracking the performance by adjusting the block size and the \emph{maxrregcount} compiler option.
+We first remove the intermediate variables to reduce the number of registers per thread.
+Then we dynamically track the performance by adjusting the block size and the \emph{maxrregcount} compiler option.
 
-Thirdly, we design a computation and communication overlapping scheme to maximize the concurrency of different resources.
-The entire wavefield domain is divided into 4 subdomain, each assigning to a GPU shown in Figure \ref{fig:domain-decomposition}.
-Note that we need ghost cells to store and exchanges the halos, denoted by the arrows.
-In each subdomain, we further divide it into three parts, the halo part, the outer part and the inner part shown in Figure \ref{fig:task-decomposition}.
+Thirdly, we design a computation and communication overlapping scheme to maximize the utilization of different kinds of resources.
+The entire wavefield domain is divided into 4 subdomains, each assigning to a GPU shown in Figure \ref{fig:domain-decomposition}.
+Note that we need ghost cells to store and exchange the halos, denoted by the arrows.
+In each subdomain, we further divide it into three parts, the halo part, the outer part and the inner part as shown in Figure \ref{fig:task-decomposition}.
 The computation of inner and outer parts are assigned to different CUDA streams so that they are executed concurrently.
 When the computation of the outer part is finished, the GPU starts exchanging halos with its neighbors.
-In this way, the computation of the inner part can hide the communication shown in Figure \ref{fig:overlap}.
+In this way, the computation of the inner part can hide the communication time perfectly, shown in Figure \ref{fig:overlap}.
 
@@
 Apart from the GPU-based optimization, we also apply another two approaches to further improve the performance.
-After we taking the energy attenuation into consideration, we can ignore the frequencies that have attenuated.
-As a result, the grid cells and the time steps get larger as the wavefield propagate in time.
-We can achieve significant speedup when we resample the velocities and wavefields to coarser grids, especially recording the longer time step.
+(1) After taking the energy attenuation into consideration, we can ignore the frequencies that have attenuated.
+Therefore, the grid cells and the time steps can get larger as the wavefields propagate in time.
+We can achieve significant speedup when we resample the velocities and wavefields to coarser grids, especially in longer time steps.
 Using the above approach, the early time steps dominate the computation.
-We eliminate the bottleneck by applying another trick that we recognize that it is not necessary to propagate the wavefields significantly away from the source at early times.
-We eliminate the update of the wavefields where the waves have not reached so far.
+(2) We eliminate the bottleneck by applying another trick that it is not necessary to propagate the wavefields significantly away from the source at early times.
+So the update of the wavefields where the waves have not reached so far is eliminated.
 
@@
 \subsection{Q Effects}
-Experiments for demonstrating the functionality of applying the Q effects as well as  the performance with different optimization tricks are carried out in this paper.
-Figure \ref{fig:with-attenuation} shows a slice of the z-component of the 3D wavefield using standard elastic wave equation at time 0.9 seconds while the Figure \ref{fig:without-attenuation} shows the wavefields with the constant Q effect ($Q_s=Q_p=20$) added.
-The wave front in Figure \ref{fig:with-attenuation} is weaker.
-The spectrum of the wavefields gives a better illustration, which is shown in Figure \ref{fig:spectrum}.
+Experiments for demonstrating the functionality of applying the Q effect as well as  the performance with different optimization strategies are presented.
+Figure \ref{fig:with-attenuation} shows the z-x pane of the z-component of the 3D wavefield using standard elastic wave equation at time 0.9 second while the Figure \ref{fig:without-attenuation} shows the wavefields with the constant Q ($Q_s=Q_p=20$) added at the same time step.
+We can see that the wavefields are nearly identical except that the wavefront in Figure \ref{fig:with-attenuation} is weaker, which is reasonable owning to the energy attenuation.
+The spectrums of the wavefields give a better illustration for the attenuation, which is shown in Figure \ref{fig:spectrum}.
 
@@
 Figure \ref{fig:gpu-speedup} shows the performance speedup of 1-4 K40 GPUs over one 24-core CPU node.
-The GPU design among 4 K40 accelerator cards can improve the performance of the computational part by up to 96 times, and improve the overall performance by up to 63 times.
-Note that the CPU design is also tuned by using multi-threading and vectorization.
-Figure \ref{fig:q-speedup} shows the speedup factor, which is  defined as the number of grid cells times time steps, as a function of propagation time for different Q values.
-We can see that the longer the time records, we more significant performance speedup we achieve.
-Combing the two tricks as well as the GPU-based optimizations, we can achieve a performance speedup over 60 to 200 times as a function of Q.
+The GPU design among 4 K40 GPUs can significantly improve the performance of the computational part by 96 times, and improve the overall performance by 63 times.
+Note that the CPU design is also well tuned by using multi-threading and vectorization.
+Figure \ref{fig:q-speedup} shows the speedup as a function of propagation time for different Q values.
+We can see that we obtain a great performance gain at early and late time because we restrict the computing region at early time and ignore the high frequencies at late time.
+The longer the time records, the more significant speedup we achieve.
+Combing the all optimization schemes as well as the GPU-based optimizations, we can achieve a performance speedup of 60x to 200x as a function of Q.
 
@@
         \includegraphics[height=1.5in]{./fig/speedup_q.eps}
-        \caption{Speedup of different Q value}
+        \caption{Speedup as different Q value}
         \label{fig:q-speedup}
     \end{subfigure}
-    \caption{Performance speedup}
+    \caption{Performance result of GPU optimizations and energy attenuation}
 \end{figure}
@@
 
-This work manages to boost the performance the wave propagation in 3D elastic scenarios by approximating the Q propagation and using GPU platforms.
-We first extends the constant-Q formulation from the 2D viscoelastic to 3D viscoelastic case.
-Different optimization techniques on GPUs are then described for a high performance modeling kernel.
-We also propose a set of tricks to reduce the computation to further reduce computations.
-The experimental results show that we can achieve significant performance speedup by 60 to 200 times over the CPU-based solution.
+This work manages to boost the performance the wavefield propagation in 3D elastic scenarios by approximating the Q propagation and the using multi-GPU platform.
+We first extend the constant-Q formulation from the 2D viscoelastic to the 3D viscoelastic case.
+Different optimization techniques on GPUs are then described for an efficient modeling kernel.
+We also propose a set of schemes to reduce the computation to further improve performance.
+The experimental results show that we can achieve significant performance speedup of 60 to 200 times with 4 GPUs over the CPU-based solution as a function of Q.
 

### 2017-01-01 paper/paris17/paper.tex
fix grammar errors by Grammarly

@@
 In recent decades there has been a significant increase of interest in the seismic exploration community to invert the image of the subsurface in larger regions and higher resolutions in the elastic media, which brings tremendous computing challenges.
-As a result the optimizing methods for improving the performance of the wavefield propagation are in great demands.
+As a result, the optimizing methods for improving the performance of the wavefield propagation are in great demands.
 
@@
 
-One approach to improve the performance of modeling is to recognize that the Earth attenuates seismic energy.
+One approach to improving the performance of modeling is to recognize that the Earth attenuates seismic energy.
 We can ignore higher and higher frequencies and still obtain an accurate image\cite[]{Clapp.sep.111.bob3} when we push the wavefield down in depth.
@@
 
-The concept of the constant Q model introduced by \cite{Kjartansson.sep.23} are used to approximate the attenuation.
-However, the formulation for computing the time derivative for the constant Q model requires to store wavefields from previous values to present time \cite[]{podlubny1998fractional}, which is impractical for real seismic modeling in terms of memory capacities on modern computers.
-Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoids the need of storing the past values of the wavefields \cite[]{zhu2014theory}.
+The concept of the constant-Q model introduced by \cite{Kjartansson.sep.23} is used to approximate the attenuation.
+However, the formulation for computing the time derivative of the constant-Q model requires to store wavefields from previous values to present time \cite[]{podlubny1998fractional}, which is impractical for real seismic modeling in terms of memory capacities on modern computers.
+Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory}.
 However, the proposed method is for 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.
@@
 
-%\subsection{Modeling}
-
-%Explicit finite difference modeling is constrained by figuring  out a sampling in time and space that results in stable propagation and does not create dispersive events.
-For stability the Courant-Friedrichs-Lewy condition \cite[]{courant1967partial} must be met.
-For stability, we have $v_{max}\frac{dt}{d_{min}} < .5$, where  $v_{max}$ is the maximum velocity; $dt$ is the
-
-%Stability is a function of limiting what percentage of a grid cell energy can move in one time step.
-Stability is therefore a function of the maximum velocity $v_{max}$, the minimum spatial sampling $d_{min}$, and the time step $dt$.
-
-%The stability condition pushes one to use larger spatial sampling (faster, but less resolution) and/or finer time sampling (more expensive).
-Dispersion, on the other hand, is a function of the minimum velocity $v_{min}$, the maximum frequency $f_{max}$, and the maximum spaital sampling $d_{max}$.
-To avoid grid dispersion we need to  sample a given frequency with a minimum number of points.
-There isn't a consensus on the minimum number
-%of points. For the purpose of this paper I will require  3.2  points therefore, we have $\frac{v_{min} }{f_{max}d_{max}} > 3.2 \label{eq:dispersion}$.
-
-%The dispersion constraint pushes us towards smaller (more expensive) spatial sampling, because of the stability constraint, and results in smaller the steps.
-Minimizing dispersion is the real reason for the expense of finite differences.
-To avoid grid dispersion and achieve the same level of stability the number of operations increase by the fourth power (three due to space sampling and one for time).
-
-%Attenuation varies as a function of frequency and earth materials.
-The first approximation I am going to use is the concept of the constant Q model introduced by \cite{Kjartansson.sep.23}.
-Q is defined as $Q=2 \pi \left( \frac{E}{\partial E}\right)$, where $\frac{E}{\partial E}$ is the fraction of energy lost per cycle.
-The larger the $Q$ value, the less energy loss per cycles.
-The constant Q assumption assumes that energy dies out is a function of the number of wavelengths traveled through a medium.
-The higher the frequency, the faster the energy is attenuated.
-
 \subsection{Constant Q formulation}
@@
 Note that the Laplacian differential operators of fractional order bring extra computational costs to the elastic modeling, we approximate it with the conventional Laplacian operators, which significantly reduces the computing complexities.
-Also, we further reduce the computational costs by ignoring the dispersion terms because it make little effects compared to the attenuation of the signals.
+Also, we further reduce the computational costs by ignoring the dispersion terms because it makes little effects compared to the attenuation of the signals.
 As a result, our equations are as follows.
@@
 For the 8th-order stencil computation, we configure the first-level cache by setting the sizes of shared memory and L1 cache to be 48 KB and 16 KB respectively, which achieves great performance based on the 3D stencil design proposed by \cite{micikevicius20093d}.
-For others, we prefer to configure the first-level cache as L1 cache where we don't use shared memory explicitly.
+For others, we prefer to configure the first-level cache as the L1 cache where we don't use shared memory explicitly.
 
@@
 \subsection{Q Effects}
-Experiments for demonstrating the functionality of applying the Q effect as well as  the performance with different optimization strategies are presented.
-Figure \ref{fig:with-attenuation} shows the z-x pane of the z-component of the 3D wavefield using standard elastic wave equation at time 0.9 second while the Figure \ref{fig:without-attenuation} shows the wavefields with the constant Q ($Q_s=Q_p=20$) added at the same time step.
+Experiments for demonstrating the functionality of applying the Q effect and the performance with different optimization strategies are presented.
+Figure \ref{fig:with-attenuation} shows the z-x plane of the z-component of the 3D wavefield using standard elastic wave equation at time 0.9 second while the Figure \ref{fig:without-attenuation} shows the wavefields with the constant Q ($Q_s=Q_p=20$) added at the same time step.
 We can see that the wavefields are nearly identical except that the wavefront in Figure \ref{fig:with-attenuation} is weaker, which is reasonable owning to the energy attenuation.
@@
 Figure \ref{fig:q-speedup} shows the speedup as a function of propagation time for different Q values.
-We can see that we obtain a great performance gain at early and late time because we restrict the computing region at early time and ignore the high frequencies at late time.
+We can see that we obtain a great performance gain at the early and late time steps because we restrict the computing region at the early time steps and ignore the high frequencies at the late time steps.
 The longer the time records, the more significant speedup we achieve.
-Combing the all optimization schemes as well as the GPU-based optimizations, we can achieve a performance speedup of 60x to 200x as a function of Q.
+Combing all optimization schemes as well as the GPU-based optimizations, we can achieve a performance speedup of 60x to 200x as a function of Q.
 

### 2017-01-02 paper/paris17/paper.tex
Weijia revise it

@@
 
-%As the Earth attenuates the seismic signals in real Earth materials, an accuracy wavefield modeling approach needs to account for the effects of attenuation and velocity dispersion \cite[]{zhu2014theory}.
-
 One approach to improving the performance of modeling is to recognize that the Earth attenuates seismic energy.
@@
 Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory}.
-However, the proposed method is for 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.
+However, the proposed method is for the 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.
 
-Meanwhile, the Nvidia Graphic Processing Units (GPUS)  have achieved a great success in many domains.
+Meanwhile, the Nvidia Graphic Processing Units (GPUs)  have achieved a great success in many domains.
 In seismic applications, GPUs are employed as high-performance computing accelerators for key seismic modeling, imaging and inversion kernels due to their high memory bandwidth and a large number of processing units \cite[]{he2015gpu}.
@@
 Note that the Laplacian differential operators of fractional order bring extra computational costs to the elastic modeling, we approximate it with the conventional Laplacian operators, which significantly reduces the computing complexities.
-Also, we further reduce the computational costs by ignoring the dispersion terms because it makes little effects compared to the attenuation of the signals.
+Also, we further reduce the computational costs by ignoring the dispersion terms because it makes little effects compared with the attenuation of the signals.
 As a result, our equations are as follows.
@@
 where $\sigma$ is the stress tensor; $\epsilon$ is the strain tensor; $c_{ij}$ is the forth-order stiffness tensor; $C_p$ and $C_s$ are the velocities of P-wave and S-wave.
-$Q_{p,s}$ is the constant factor for the attenuation of P-wave and S-wave respectively.
-Note that we only present how $\tau_p^{(1)}$ and $\tau_s^{(1)}$ are derived, $\tau_p^{(2)}$,$\tau_p^{(3)}$, $\tau_s^{(2)}$ and $\tau_s^{(3)}$ can be derived in a similar way.
+$Q_{p,s}$ is the constant factor for the attenuation of P-wave and S-wave, respectively.
+Note that we only present how $\tau_p^{(1)}$ and $\tau_s^{(1)}$ are derived$.
+\tau_p^{(2)}$,$\tau_p^{(3)}$, $\tau_s^{(2)}$ and $\tau_s^{(3)}$ can be derived in a similar way.
 
@@
 
-The reason why GPUs outperforms CPUs significantly on many scenarios is that the architecture of GPUs favors the throughput of many data-parallel tasks over the latency of a single thread.
+The reason why GPUs outperform CPUs significantly on many scenarios is that the architecture of GPUs favors the throughput of many data-parallel tasks over the latency of a single thread.
 We have an efficient parallel design on the multiple-GPU platform with three main strategies.
@@
 As the 64KB first-level cache can be configured as different combinations between L1 cache and shared memory, we configure it dynamically in different scenarios.
-For the 8th-order stencil computation, we configure the first-level cache by setting the sizes of shared memory and L1 cache to be 48 KB and 16 KB respectively, which achieves great performance based on the 3D stencil design proposed by \cite{micikevicius20093d}.
+For the 8th-order stencil computation, we configure the first-level cache by setting the sizes of shared memory and L1 cache to 48 KB and 16 KB, respectively, which achieves great performance based on the 3D stencil design proposed by \cite{micikevicius20093d}.
 For others, we prefer to configure the first-level cache as the L1 cache where we don't use shared memory explicitly.
@@
 The entire wavefield domain is divided into 4 subdomains, each assigning to a GPU shown in Figure \ref{fig:domain-decomposition}.
-Note that we need ghost cells to store and exchange the halos, denoted by the arrows.
+Note that we need ghost cells to store and exchange the halos, which is denoted by the arrows.
 In each subdomain, we further divide it into three parts, the halo part, the outer part and the inner part as shown in Figure \ref{fig:task-decomposition}.
-The computation of inner and outer parts are assigned to different CUDA streams so that they are executed concurrently.
+The computation of inner and outer parts is assigned to different CUDA streams so that they are executed concurrently.
 When the computation of the outer part is finished, the GPU starts exchanging halos with its neighbors.
@@
 Experiments for demonstrating the functionality of applying the Q effect and the performance with different optimization strategies are presented.
-Figure \ref{fig:with-attenuation} shows the z-x plane of the z-component of the 3D wavefield using standard elastic wave equation at time 0.9 second while the Figure \ref{fig:without-attenuation} shows the wavefields with the constant Q ($Q_s=Q_p=20$) added at the same time step.
-We can see that the wavefields are nearly identical except that the wavefront in Figure \ref{fig:with-attenuation} is weaker, which is reasonable owning to the energy attenuation.
+Figure \ref{fig:with-attenuation} shows the z-x plane of the z-component of the 3D wavefield using standard elastic wave equation at 0.9 seconds while Figure \ref{fig:without-attenuation} shows the wavefields with the constant Q ($Q_s=Q_p=20$) added at the same time step.
+We can observe that the wavefields are nearly identical except that the wavefront in Figure \ref{fig:with-attenuation} is weaker, which is reasonable owning to the energy attenuation.
 The spectrums of the wavefields give a better illustration for the attenuation, which is shown in Figure \ref{fig:spectrum}.
@@
 The longer the time records, the more significant speedup we achieve.
-Combing all optimization schemes as well as the GPU-based optimizations, we can achieve a performance speedup of 60x to 200x as a function of Q.
+Combining all optimization schemes as well as the GPU-based optimizations, we can achieve a performance speedup of 60x to 200x as a function of Q.
 
@@
     \end{subfigure}
-    \caption{Performance result of GPU optimizations and energy attenuation}
+    \caption{Performance results of GPU optimizations and energy attenuation}
 \end{figure}
@@
 
-This work manages to boost the performance the wavefield propagation in 3D elastic scenarios by approximating the Q propagation and the using multi-GPU platform.
-We first extend the constant-Q formulation from the 2D viscoelastic to the 3D viscoelastic case.
+This work manages to boost the performance of the wavefield propagation in 3D elastic scenarios by approximating the Q propagation and using the multi-GPU platform.
+We first extend the constant-Q formulation from the 2D viscoelastic case to the 3D viscoelastic case.
 Different optimization techniques on GPUs are then described for an efficient modeling kernel.
-We also propose a set of schemes to reduce the computation to further improve performance.
-The experimental results show that we can achieve significant performance speedup of 60 to 200 times with 4 GPUs over the CPU-based solution as a function of Q.
+We also propose a set of schemes to reduce the computation to further improve the performance.
+The experimental results show that we can achieve significant performance speedups of 60 to 200 times with 4 GPUs over the CPU-based solution as a function of Q.
 

### 2017-01-03 paper/paris17/paper.tex
fix citation

@@
 The concept of the constant-Q model introduced by \cite{Kjartansson.sep.23} is used to approximate the attenuation.
-However, the formulation for computing the time derivative of the constant-Q model requires to store wavefields from previous values to present time \cite[]{podlubny1998fractional}, which is impractical for real seismic modeling in terms of memory capacities on modern computers.
-Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory}.
+However, the formulation for computing the time derivative of the constant-Q model requires to store wavefields from previous values to present time, which is impractical for real seismic modeling in terms of memory capacities on modern computers.
+Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory,shen2013wave,shen2015image}.
 However, the proposed method is for the 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.

### 2017-01-03 paper/paris17/paper.tex
Yi Shen revise it

@@
 However, the formulation for computing the time derivative of the constant-Q model requires to store wavefields from previous values to present time, which is impractical for real seismic modeling in terms of memory capacities on modern computers.
-Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory,shen2013wave,shen2015image}.
+Zhu developed a constant-Q wave equation using fractional Laplacian operators which avoid the need for storing the past values of the wavefields \cite[]{zhu2014theory,shen2013wave}.
 However, the proposed method is for the 2D viscoelastic case and the computational cost of fractional Laplacian is still expensive compared with the conventional Laplacian.
@@
 The stress-strain relation is derived from the classical equation expressed in terms of fractional time derivatives.
-The formulation has the advantage of not requiring additional field variables so that it saves the computing time and storage significantly \cite[]{zhu2014theory}.
+The formulation has the advantage of not requiring additional field variables so that it saves the computing time and storage significantly.
 
 We extend the formulation of \cite{zhu2014theory} from the 2D viscoelastic case to the 3D viscoelastic case.
-Note that the Laplacian differential operators of fractional order bring extra computational costs to the elastic modeling, we approximate it with the conventional Laplacian operators, which significantly reduces the computing complexities.
-Also, we further reduce the computational costs by ignoring the dispersion terms because it makes little effects compared with the attenuation of the signals.
+Note that the Laplacian differential operators of fractional order bring extra computational costs to the elastic modeling, we approximate it with the conventional Laplacian operators, which not only significantly reduces the computing complexities but also preserves the accuracy if Q is not extremely low \cite[]{shen2015image}.
+We further reduce the computational costs by ignoring the dispersion terms because it makes little effects compared with the attenuation of the signals.
 As a result, our equations are as follows.
